O/Tet3 rmRNA - clustering
========================================================

How general is the positive correlation between 5hmC and expression in Tet3-tg mOSNs?
Do clusters exist on against-trend genes

Cluster genes by gene body 5hmC principal componenets and rmRNA fold change

1. Prcomp on ott3 - omp difference matrix within gene body
2. Predict and extract PC1 and PC2
3. Combine with rmRNA fold change data

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
```

```{r}
omp.hmc.pos <- makeImage("omp_hmc_120424_rpkm", "gene_whole_W200N50F50_chr",  data_type="rpkm/mean", image=FALSE)
ott3.hmc.pos <- makeImage("ott3_1_hmc_rpkm", "gene_whole_W200N50F50_chr",  data_type="rpkm/mean", image=FALSE)
ott3.omp.hmc.pos <- ott3.hmc.pos - omp.hmc.pos
```

```{r}
ott3.omp.hmc.pos.pc <- prcomp(ott3.omp.hmc.pos[,51:100])
ott3.omp.hmc.pos.pred <- predict(ott3.omp.hmc.pos.pc, ott3.omp.hmc.pos)
ott3.omp.hmc.pos.pc1 <- ott3.omp.hmc.pos[order(ott3.omp.hmc.pos.pred[,1]),]
ott3.omp.hmc.pos.pc2 <- ott3.omp.hmc.pos[order(ott3.omp.hmc.pos.pred[,2]),]
```


```{r}
rna <- readRDS("~/s2/analysis/rna/rdata/omp_ott3_rmrna_masked_uq_1log2.rds")
```

```{r}
m <- match(rownames(ott3.omp.hmc.pos.pred), rna$gene)
comb <- na.omit(cbind(ott3.omp.hmc.pos.pred[,1:2], rna.ott3.omp=rna$ott3.omp[m]))
```

```{r}
cor(comb)
```

```{r}
library(IDPmisc)
ipairs(comb, ztransf=log)
```

### Hierarchical clustering
```{r}
library(cluster)
```

```{r}
comb.scale <- scale(comb)
```
```
comb.eu <- dist(comb.scale)
comb.ag <- agnes(comb.eu)
saveRDS(comb.ag, file="~/s2/analysis/cluster/hclust/ott3_omp_hmc_gene_whole_body_pc1_2_rmrna_fc_eu_agnes.rds")
```

```
comb.ag.ward <- agnes(comb.eu, method="ward")
saveRDS(comb.ag, file="~/s2/analysis/cluster/hclust/ott3_omp_hmc_gene_whole_body_pc1_2_rmrna_fc_eu_agnes_ward.rds")
```

