Omp-tTA X tetO-Tet3 ribominus-RNA analysis
========================================================

Extract FPKM values from Cuffdiff output
```
cd <- read.delim("~/s2/data/rna/cuffdiff/omp_ott3_rmrna/gene_exp.diff")
rna <- cd[,c("value_1", "value_2")]
```

Average entries with common gene names
```
library(plyr)
rna[,3] <- cd$gene
colnames(rna) <- c("omp", "ott3", "gene")
rna.s <- ddply(rna, .(gene), summarize, omp=mean(omp), ott3=mean(ott3), .progress="text")
rownames(rna.s) <- rna.s$gene
rna.s <- rna.s[,c(2,3)]
rna.1log2 <- colwise(function(x) log2(x+1))(rna.s)
rownames(rna.1log2) <- rownames(rna.s)
rna.1log2$ott3.omp <- with(rna.1log2, ott3-omp)
saveRDS(rna.1log2, file="~/s2/analysis/rna/rdata/omp_ott3_rmrna_1log2.rds")
```

Above prep performed with repeat masked, upper quartile compatible normed
```
cd3 <- read.delim("~/s2/data/rna/cuffdiff/omp_ott3_rmrna_masked_uq_comp_js/gene_exp.diff")
```

Slight reduction in the FPKM of more lowly transcribed genes
```{r}
rna3.1log2 <- readRDS("~/s2/analysis/rna/rdata/omp_ott3_rmrna_masked_uq_1log2.rds")
rna4 <- data.frame(omp1=rna.1log2$omp, ott31=rna.1log2$ott3, omp3=rna3.1log2$omp[match(rna.1log2$id, rna3.1log2$gene)], ott33=rna3.1log2$ott3[match(rna.1log2$id, rna3.1log2$gene)])
gg <- ggplot(rna4, aes(omp1, omp3))
gg + geom_point(alpha=I(1/5))
gg <- ggplot(rna4, aes(ott31, ott33))
gg + geom_point(alpha=I(1/5))

```



```{r, fig.width=9, fig.height=6}
rna.1log2 <-readRDS("~/s2/analysis/rna/rdata/omp_ott3_rmrna_1log2.rds")
par(mfrow=c(1,3))
a <- apply(rna.1log2, 2, function(x) plot(density(x)))

```

Scatter OMP and O/TT3 log2(FPKM+1).

```{r, fig.width=4, fig.height=4}
library(ggplot2)
gg <- ggplot(rna.1log2, aes(omp, ott3))
gg + geom_point(alpha=I(1/10)) + geom_abline(slope=1, intercept=0, linetype=2)
```

Import DNA modification levels, calculated from 2 to 7 kb downstream of TSS.
```{r}
dna <- readRDS("~/s2/analysis/features/norm/rpkm/mean/rdata/tt3_min_refgene_nodup_TSS2to7kb_hmc_mc_scores_rm_outliers_clean.rds")
```

Combine with RNA data
```{r}
comb <- dna
comb$rmrna.omp <- rna.1log2[match(rownames(comb), rownames(rna.1log2)),1]
comb$rmrna.tt3 <- rna.1log2[match(rownames(comb), rownames(rna.1log2)),2]
comb <- na.omit(comb)
dim(comb)
```

Pearson and Spearman correlations
```{r}
cor(comb)
cor(comb, method="spearman")
```

Compute ratio scores
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/features.R"))
comb <- transform(comb, 
                  hmc.tt3.omp = computeScoreRatios(hmc.tt3, hmc.omp), 
                  mc.tt3.omp = computeScoreRatios(mc.tt3, mc.omp),
                  rmrna.tt3.omp = rmrna.tt3-rmrna.omp)
cor(comb)
cor(comb, method="spearman")

```

Plot rmRNA ratio versus 5hmC score 
```{r, fig.width=6, fig.height=4}
gg <- ggplot(comb, aes(hmc.tt3.omp, rmrna.tt3.omp))
gg <- gg + geom_point(alpha=I(1/10)) + coord_cartesian(ylim=c(-5, 5)) + xlab("OTT3 / OMP 5hmC ratio") + ylab("OTT3 / OMP RNA ratio")
gg + stat_smooth(method="lm") + annotate("text", x=1.5, y=4, label="Pearson R = 0.13")
```

Split genes by gain or loss of 5hmC, and plot boxplot of rmRNA ratio
#```{r, fig.width=4, fig.height=6}
#rna.1log2.m$hmc <- "No change"
#rna.1log2.m$hmc[rna.1log2.m$id %in% rownames(comb[comb$hmc.tt3.omp>0.2,])] <- "Increased"
#rna.1log2.m$hmc[rna.1log2.m$id %in% rownames(comb[comb$hmc.tt3.omp<0.2,])] <- "Decreased"
#hmc.levels <- factor(1:3, labels=c("Decreased", "No change", "Increased"))
#rna.1log2.m$hmc <- hmc.levels[match(rna.1log2.m$hmc, as.character(hmc.levels))]
#levels(rna.1log2.m$variable) <- c("OMP", "O/TT3", "O/TT3 vs OMP")
#gg <- ggplot(rna.1log2.m[rna.1log2.m$variable!="O/TT3 vs OMP",], aes(hmc, value, fill=variable))
#gg <- gg + geom_boxplot(outlier.size=0) + coord_cartesian(ylim=c(0,8)) + scale_fill_grey(name="", start=.4, end=.8) + xlab("O/TT3 vs. OMP 5hmC") + #ylab("log2(FPKM + 1)")
#gg

#gg <- ggplot(rna.1log2.m[rna.1log2.m$variable=="O/TT3 vs OMP",], aes(hmc, value, fill=variable))
#gg <- gg + geom_boxplot(outlier.size=0) + coord_cartesian(ylim=c(0,2)) + scale_fill_grey(name="", start=.4, end=.8) + xlab("O/TT3 vs. OMP 5hmC") + #ylab("log2(FPKM + 1)")
#gg
#```

### 5hmC heatmaps 
Load omp, o/tt3 hmc gene position matrices
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
omp.hmc.pos <- makeImage("omp_hmc_120424_rpkm", "gene_whole_W200N50F50_chr",  data_type="rpkm/mean", image=FALSE)
ott3.hmc.pos <- makeImage("ott3_1_hmc_rpkm", "gene_whole_W200N50F50_chr",  data_type="rpkm/mean", image=FALSE)
ott3.omp.hmc.pos <- ott3.hmc.pos - omp.hmc.pos
```

Principal components analysis on gene body to order
```{r}
omp.hmc.pos.pc <- prcomp(omp.hmc.pos[,51:100])
ott3.hmc.pos.pc <- prcomp(ott3.hmc.pos[,51:100])
omp.hmc.pos.pred <- predict(omp.hmc.pos.pc, omp.hmc.pos[,51:100])
ott3.hmc.pos.pred <- predict(ott3.hmc.pos.pc, ott3.hmc.pos[,51:100])

omp.hmc.pos.pc1 <- omp.hmc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(omp.hmc.pos)),]
ott3.hmc.pos.pc1 <- ott3.hmc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(ott3.hmc.pos)),]
omp.hmc.pos.ott3.pc1 <- omp.hmc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(omp.hmc.pos)),]
ott3.hmc.pos.omp.pc1 <- ott3.hmc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(ott3.hmc.pos)),]
```

Order difference matrix
```{r}
ott3.omp.hmc.pos.omp.pc1 <- na.omit(ott3.omp.hmc.pos[match(rownames(omp.hmc.pos.pc1), rownames(ott3.omp.hmc.pos)),])
ott3.omp.hmc.pos.ott3.pc1<- na.omit(ott3.omp.hmc.pos[match(rownames(ott3.hmc.pos.pc1), rownames(ott3.omp.hmc.pos)),])
```


Compare orders with RNA
```{r}
rna.1log2.omp.pc1 <- na.omit(rna.1log2[match(rownames(omp.hmc.pos.pc1), rownames(rna.1log2)),])
rna.1log2.ott3.pc1 <- na.omit(rna.1log2[match(rownames(ott3.hmc.pos.pc1), rownames(rna.1log2)),])

```

Group in 100 chunks
```{r}
ott3.omp.hmc.pos.omp.pc1.c100 <- foreach(c=isplitRows(ott3.omp.hmc.pos.omp.pc1[,51:100], chunks=100), .combine="rbind") %do% mean(c, na.rm=TRUE)
ott3.omp.hmc.pos.omp.pc1.c100 <- as.data.frame(ott3.omp.hmc.pos.omp.pc1.c100)
ott3.omp.hmc.pos.omp.pc1.c100$index <- 100:1
ott3.omp.hmc.pos.ott3.pc1.c100 <- foreach(c=isplitRows(ott3.omp.hmc.pos.ott3.pc1[,51:100], chunks=100), .combine="rbind") %do% mean(c, na.rm=TRUE)
ott3.omp.hmc.pos.ott3.pc1.c100 <- as.data.frame(ott3.omp.hmc.pos.ott3.pc1.c100)
ott3.omp.hmc.pos.ott3.pc1.c100$index <- 100:1

rna.1log2.omp.pc1.c100 <- foreach(c=isplitRows(rna.1log2.omp.pc1[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.omp.pc1.c100 <- as.data.frame(rna.1log2.omp.pc1.c100)
rna.1log2.omp.pc1.c100$index <- 100:1
rna.1log2.ott3.pc1.c100 <- foreach(c=isplitRows(rna.1log2.ott3.pc1[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.ott3.pc1.c100 <- as.data.frame(rna.1log2.ott3.pc1.c100)
rna.1log2.ott3.pc1.c100$index <- 100:1
```

#### Plot heatmaps
```{r "gene_whole_W200N50F50_omp_hmc_120424_rpkm_mean_ordered_by_gene_body_pc1", fig.height=6, fig.width=6,dev=c('png', 'pdf')}
MP.heat(omp.hmc.pos.pc1, range=c(0,1.5), average=50)
```

```{r "gene_whole_W200N50F50_ott3_1_hmc_rpkm_mean_ordered_by_omp_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.hmc.pos.omp.pc1, range=c(0,1.5), average=50)
```

O/TT3 - OMP gene body 5hmC ordered by OMP 5hmC PC1
```{r "ott3_sub_omp_gene_body_hmc_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(ott3.omp.hmc.pos.omp.pc1.c100, aes(V1, index))
gg + geom_point() + xlab("RPM") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(-2, .5))
```

OMP rmRNA ordered by OMP 5hmC PC1
```{r "omp_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.omp.pc1.c100, aes(omp, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4))
```

O/TT3 rmRNA ordered by OMP 5hmC PC1
```{r "ott3_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.omp.pc1.c100, aes(ott3, index))
gg <- gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4))
gg
```

O/TT3 - OMP rmRNA ratio ordered by OMP 5hmC PC1
```{r "ott3_omp_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.omp.pc1.c100, aes(ott3.omp, index))
gg <- gg + geom_vline(xintercept=0, color="red")
gg <- gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + labs(title=c("O/Tet3-OMP ratio RNA by OMP PC1"))
gg
```

```{r "gene_whole_W200N50F50_omp_hmc_120424_rpkm_mean_ordered_by_ott3_1_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(omp.hmc.pos.ott3.pc1, range=c(0,1.5), average=50)
```

```{r "gene_whole_W200N50F50_ott3_1_hmc_rpkm_mean_ordered_by_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.hmc.pos.pc1, range=c(0,1.5), average=50)
```

O/TT3 - OMP gene body 5hmC ordered by O/TT3 5hmC PC1
```{r "ott3_sub_omp_gene_body_hmc_1log2_ordered_by_ott3_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(ott3.omp.hmc.pos.ott3.pc1.c100, aes(V1, index))
gg + geom_point() + xlab("RPM") + ylab("") + theme(axis.text.y=element_blank()) +  coord_cartesian(xlim=c(-.5, 1))
```

OMP rmRNA ordered by O/TT3 5hmC PC1
```{r "omp_rmrna_1log2_ordered_by_ott3_1_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(omp, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4)) + labs(title=c("OMP RNA by O/Tet3 PC1"))
```

O/TT3 rmRNA ordered by O/TT3 5hmC PC1
```{r "ott3_rmrna_1log2_ordered_by_ott3_1_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(ott3, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4)) + labs(title=c("O/Tet3 RNA by O/Tet3 PC1"))
```

Plot O/TT3 - OMP rmRNA ratio ordered by O/TT3 5hmC PC1
```{r "ott3_omp_rmrna_1log2_ordered_by_ott3_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(ott3.omp, index))
gg <- gg + geom_vline(xintercept=0, color="red")
gg <- gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + labs(title=c("O/Tet3-OMP ratio RNA by O/Tet3 PC1"))
gg
```


### 5mC heatmaps 
Load omp, o/tt3 mc gene position matrices
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
omp.mc.pos <- makeImage("omp_mc_rpkm", "gene_whole_W200N50F50_chr",  data_type="rpkm/mean", image=FALSE)
ott3.mc.pos <- makeImage("ott3_1_mc_rpkm", "gene_whole_W200N50F50_chr",  data_type="rpkm/mean", image=FALSE)
ott3.omp.mc.pos <- ott3.mc.pos - omp.mc.pos
```

Principal components analysis on gene body to order
```{r}
omp.mc.pos.pc <- prcomp(omp.mc.pos[,51:100])
ott3.mc.pos.pc <- prcomp(ott3.mc.pos[,51:100])
omp.mc.pos.pred <- predict(omp.mc.pos.pc, omp.mc.pos[,51:100])
ott3.mc.pos.pred <- predict(ott3.mc.pos.pc, ott3.mc.pos[,51:100])

omp.mc.pos.pc1 <- omp.mc.pos[match(rownames(omp.mc.pos.pred[order(omp.mc.pos.pred[,1]),]), rownames(omp.mc.pos)),]
ott3.mc.pos.pc1 <- ott3.mc.pos[match(rownames(ott3.mc.pos.pred[order(ott3.mc.pos.pred[,1]),]), rownames(ott3.mc.pos)),]
ott3.mc.pos.omp.pc1 <- ott3.mc.pos[match(rownames(omp.mc.pos.pred[order(omp.mc.pos.pred[,1]),]), rownames(ott3.mc.pos)),]
```

Ordering
```{r}
omp.mc.pos.omp.hmc.pc1 <- omp.mc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(omp.mc.pos)),]
ott3.mc.pos.omp.hmc.pc1 <- ott3.mc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(ott3.mc.pos)),]
ott3.omp.mc.pos.omp.hmc.pc1 <- ott3.omp.mc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(ott3.omp.mc.pos)),]
omp.mc.pos.ott3.hmc.pc1 <- omp.mc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(omp.mc.pos)),]
ott3.mc.pos.ott3.hmc.pc1 <- ott3.mc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(ott3.mc.pos)),]
ott3.omp.mc.pos.ott3.hmc.pc1 <- ott3.omp.mc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(ott3.omp.mc.pos)),]
```

Compare orders with RNA
```{r}
rna.1log2.omp.pc1 <- na.omit(rna.1log2[match(rownames(omp.mc.pos.pc1), rownames(rna.1log2)),])
rna.1log2.ott3.pc1 <- na.omit(rna.1log2[match(rownames(ott3.mc.pos.pc1), rownames(rna.1log2)),])
```

Group in 100 chunks
```{r}
ott3.omp.mc.pos.omp.hmc.pc1.c100 <- foreach(c=isplitRows(ott3.omp.mc.pos.omp.hmc.pc1[,51:100], chunks=100), .combine="rbind") %do% mean(c, na.rm=TRUE)
ott3.omp.mc.pos.omp.hmc.pc1.c100 <- as.data.frame(ott3.omp.mc.pos.omp.hmc.pc1.c100)
ott3.omp.mc.pos.omp.hmc.pc1.c100$index <- 100:1
ott3.omp.mc.pos.ott3.hmc.pc1.c100 <- foreach(c=isplitRows(ott3.omp.mc.pos.ott3.hmc.pc1[,51:100], chunks=100), .combine="rbind") %do% mean(c, na.rm=TRUE)
ott3.omp.mc.pos.ott3.hmc.pc1.c100 <- as.data.frame(ott3.omp.mc.pos.ott3.hmc.pc1.c100)
ott3.omp.mc.pos.ott3.hmc.pc1.c100$index <- 100:1
rna.1log2.omp.pc1.c100 <- foreach(c=isplitRows(rna.1log2.omp.pc1[,1:2], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.omp.pc1.c100 <- as.data.frame(rna.1log2.omp.pc1.c100)
rna.1log2.omp.pc1.c100$index <- 100:1
rna.1log2.ott3.pc1.c100 <- foreach(c=isplitRows(rna.1log2.ott3.pc1[,1:2], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.ott3.pc1.c100 <- as.data.frame(rna.1log2.ott3.pc1.c100)
rna.1log2.ott3.pc1.c100$index <- 100:1
```

#### Plot heatmaps

```{r "gene_whole_W200N50F50_omp_mc_rpkm_mean_ordered_by_omp_hmc_gene_body_pc1", fig.height=6, fig.width=6,dev=c('png', 'pdf')}
MP.heat(omp.mc.pos.omp.hmc.pc1, range=c(0,1), average=50)
```

```{r "gene_whole_W200N50F50_ott3_1_mc_rpkm_mean_ordered_by_omp_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.mc.pos.omp.hmc.pc1, range=c(0,1), average=50)
```

O/TT3 - OMP gene body 5mC ordered by OMP 5hmC PC1
```{r "ott3_sub_omp_gene_body_mc_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(ott3.omp.mc.pos.omp.hmc.pc1.c100, aes(V1, index))
gg + geom_point() + xlab("RPM") + ylab("") + theme(axis.text.y=element_blank()) 
```

Combine 5hmC and 5mC indices
```{r}
ott3.hmc.mc.pos.omp.hmc.pc1.c100 <- data.frame(hmc=ott3.hmc.pos.omp.pc1.c100[,1], mc=ott3.mc.pos.omp.hmc.pc1.c100[,1], index=ott3.mc.pos.omp.hmc.pc1.c100[,2])
ott3.hmc.mc.pos.omp.hmc.pc1.c100.m <- melt(ott3.hmc.mc.pos.omp.hmc.pc1.c100, id.vars=c("index"), measure.vars=c("hmc", "mc"))
ott3.omp.hmc.mc.pos.omp.hmc.pc1.c100 <- data.frame(hmc=ott3.omp.hmc.pos.omp.pc1.c100[,1], mc=ott3.omp.mc.pos.omp.hmc.pc1.c100[,1], index=ott3.omp.mc.pos.omp.hmc.pc1.c100[,2])
ott3.omp.hmc.mc.pos.omp.hmc.pc1.c100.m <- melt(ott3.omp.hmc.mc.pos.omp.hmc.pc1.c100, id.vars=c("index"), measure.vars=c("hmc", "mc"))
```

Plot together
```{r}
gg <- ggplot(ott3.omp.hmc.mc.pos.omp.hmc.pc1.c100.m, aes(value, index, color=variable))
gg + geom_point() + facet_grid(.~variable)
```



```{r "gene_whole_W200N50F50_omp_mc_rpkm_mean_ordered_by_ott3_1_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(omp.mc.pos.ott3.hmc.pc1, range=c(0,1), average=50)
```
```{r "gene_whole_W200N50F50_ott3_1_mc_rpkm_mean_ordered_by_ott3_1_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.mc.pos.ott3.hmc.pc1, range=c(0,1), average=50)
```

O/TT3 - OMP gene body 5hmC ordered by O/TT3 5hmC PC1
```{r "ott3_sub_omp_gene_body_mc_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(ott3.omp.mc.pos.ott3.hmc.pc1.c100, aes(V1, index))
gg + geom_point() + xlab("RPM") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(-.5,.5))
```




Plot OMP
```{r "omp_rmrna_1log2_ordered_by_omp_mc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.omp.pc1.c100, aes(omp, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank())
```

Plot O/TT3
```{r "ott3_rmrna_1log2_ordered_by_ott3_1_mc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(ott3, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank())
```

Order by 5hmC PC1
```{r}
omp.mc.pos.hmc.pc1 <- omp.mc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(omp.mc.pos)),]
ott3.mc.pos.hmc.pc1 <- ott3.mc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(ott3.mc.pos)),]
```
Plot heatmaps
```{r "gene_whole_W200N50F50_omp_mc_rpkm_mean_ordered_by_hmc_gene_body_pc1", fig.height=6, fig.width=6,dev=c('png', 'pdf')}
MP.heat(omp.mc.pos.hmc.pc1, range=c(0,1), average=50)
```

```{r "gene_whole_W200N50F50_ott3_1_mc_rpkm_mean_ordered_by_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.mc.pos.hmc.pc1, range=c(0,1), average=50)
```

#### Order by rmRNA levels

```{r}
comb.omp <- comb[order(-comb$rmrna.omp),]
comb.ott3 <- comb[order(-comb$rmrna.tt3),]
omp.hmc.pos.omp.rmrna <- omp.hmc.pos[match(rownames(comb.omp), rownames(omp.hmc.pos)),]
ott3.hmc.pos.ott3.rmrna <- ott3.hmc.pos[match(rownames(comb.ott3), rownames(ott3.hmc.pos)),]
omp.mc.pos.omp.rmrna <- omp.mc.pos[match(rownames(comb.omp), rownames(omp.mc.pos)),]
ott3.mc.pos.ott3.rmrna <- ott3.mc.pos[match(rownames(comb.ott3), rownames(ott3.mc.pos)),]
```

Plot heatmaps
```{r}
MP.heat(omp.hmc.pos.omp.rmrna, range=c(0,1), average=50)
```

```{r}
MP.heat(ott3.hmc.pos.ott3.rmrna, range=c(0,1), average=50)
```

```{r}
MP.heat(omp.mc.pos.omp.rmrna, range=c(0,1), average=50)
```

```{r}
MP.heat(ott3.mc.pos.ott3.rmrna, range=c(0,1), average=50)
```


### TSS levels

Read in 5mC/5hmC levels for -500 bp to +500 bp around TSS
```{r}
tss <- read.delim("~/s2/analysis/features/norm/rpkm/mean/summaries/tt3_min_refgene_-500bpTSS+500bp_chr_sqrt")
comb$hmc.omp.tss <- tss[match(rownames(comb), rownames(tss)),1]
comb$hmc.ott3.tss <- tss[match(rownames(comb), rownames(tss)),2]
comb <- na.omit(comb)
cor(comb[,c("rmrna.omp","rmrna.tt3","hmc.omp.tss","hmc.ott3.tss")], method="spearman")
```

