Developmental nucleosome positioning
========================================================

Classify silent (FPKM = 0) or expressed (top third of non-zero FPKM genes). Essentially groups 1 and 4 of 'range4' partitions.

Compute phasogram using Will's Phasogram. 'nuc_pileup_01234.trk' contains omp,ngn, mash1,icam nucleosome read starts. 'rna_range4' contains range4 data for omp, ngn, and icam FPKM data.

```
phase_batch.py -t nuc_pileup_01234.trk -b rna_range4 -n 2 -l 2000
```

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/profiles2.R"))
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/phase.R"))
```

Load phasogram output
```{r}
filters <- c("omp_nuc_0123_omp", "ngn_nuc_456_ngn", "icam_nuc_01234_icam")
pd <- lapply(filters, function(x) loadPhaseData("~/s2/analysis/nuc/phasogram/rna_range4", filter=x))
names(pd) <- c("mOSN", "GBC", "HBC")             
```

Normalize by total number of reads and end of phase plot
```{r}
pd.norm <- lapply(pd, normPhaseData)
```

Plot 1 and 4 groups 
```{r omp_ngn_icam_nuc_rna_range4_group1_4, dev=c("png", "pdf"), fig.width=9, fig.height=3}
paper_colors <- c("#99CC66", "#6095C9")
par(mfrow=c(1,3), mar=c(2, 2, 2, 2), oma=c(2, 2, 1, 1))
a <- lapply(names(pd.norm), function(x) plotPhase.pair(pd.norm[[x]][c(1,4)], phase_ind=ind16, step=1, cols=paper_colors[2:1], main=x, ylim=c(.8, 1.4), ylab="", xlab=""))
mtext("Density", side=2, outer=T, line=.5)
mtext("Phase in basepairs", side=1, outer=T, line=.5)
legend(x=1250, y=1.4, legend=c("Silent", "Expressed"), col=paper_colors[2:1], lty=1, cex=.8,bty="n")
```

```{r}
pd.norm.cells <- ldply(pd.norm, ldply)
pd.norm.cells.silent <- lapply(c(1,5,9), function(x) pd.norm.cells[x,2:2001])
pd.norm.cells.expr <- lapply(c(4,8,12), function(x) pd.norm.cells[x, 2:2001])
```

```{r omp_ngn_icam_nuc_rna_range4_group1_4_cells_together, dev=c("png", "pdf"), fig.width=8, fig.height=4}
par(mfrow=c(1,2), mar=c(2, 2, 2, 2), oma=c(2, 2, 1, 1))
plotPhase.triple(pd.norm.cells.silent, phase_ind=ind16, step=1, cols=col3, ylim=c(.8, 1.4), main="Silent")
plotPhase.triple(pd.norm.cells.expr, phase_ind=ind16, step=1, cols=col3, ylim=c(.8, 1.4), main="Expressed")
mtext("Density", side=2, outer=T, line=.5)
mtext("Phase in basepairs", side=1, outer=T, line=.5)
legend(x=1250, y=1.4, legend=c("mOSN", "GBC", "HBC"), col=col3, lty=1, cex=.8,bty="n")
```

mOSN, 
  silent : N = 2786
  expressed : N = 5452

GBC,
  silent : N = 1694
  expressed : N = 5487
  
HBC,
  silent : N = 5760
  expressed : N = 5062
  
  
### Compute phase score
```{r}
fft.mag <- lapply(pd.norm, function(x) lapply(x, phase.fft, ind16, 5))
```

```{r}
par(mfrow=c(3,4))
a <- lapply(fft.mag, function(x) lapply(x, phase.plot.fft, 5, ylim=c(0, 1000)))
```


```{r}
fft.mag.max <- lapply(fft.mag, phase.fftMax, c(5, 100))
fft.mag.max.silent.expressed <- lapply(fft.mag.max, function(x) x[c(1,4)])
fft.mag.max.silent.expressed <- ldply(fft.mag.max.silent.expressed)
colnames(fft.mag.max.silent.expressed) <- c("celltype", "silent", "expressed")
fft.mag.max.silent.expressed
```

### Compute inter-nuc distances
```{r}
peaks <- lapply(pd.norm, function(x) lapply(x, reportPhasePeaks, phase_ind=ind16))
nuc_dist <- lapply(peaks, function(x) lapply(x, slopeFromPeaks))
```

Reformat
```{r}
library(plyr)
nuc_dist.df <- ldply(nuc_dist, function(d) ldply(d))
nuc_dist.df$group <- factor(1:4, labels=c("Silent", "G2", "G3", "Expressed"))
nuc_dist.df$celltype <- rep(factor(1:3, labels=c("mOSN", "GBC", "HBC")), each=4)
nuc_dist.df
```

Plot as bar
```{r omp_ngn_icam_nuc_rna_range4_group1_and_4_peak_slopes, dev=c("png", "pdf"), fig.width=4, fig.height=6}
library(ggplot2)
theme_set(theme_bw())
gg <- ggplot(nuc_dist.df[nuc_dist.df$group=="Silent" | nuc_dist.df$group=="Expressed",], aes(celltype, index, fill=group))
gg <- gg + geom_bar(stat="identity", position="dodge") + facet_grid(.~group)
gg <- gg + theme(legend.position="none", axis.text.x=element_text(face="bold", color="black")) + labs(x="", y="Basepairs")
gg <- gg + scale_fill_manual(values=col2[2:1])
gg
```

Appears that an outlier is affected expressed HBC model fit
```{r}
# Break down slopeFromPeaks
nuc_dist <- lapply(peaks, function(x) lapply(x, function(y) data.frame(peaks=y, index=1:length(y))))
model <- lapply(nuc_dist, function(x) lapply(x, function(y) lm(peaks~index, data=y)))

# Replace HBC, expressed with model lacking outlier
model[[3]][[4]] <- lm(peaks~index, data=nuc_dist[[3]][[4]][1:6,])   
slopes <- lapply(model, function(x) lapply(x, function(y) coef(y)[2]))


# Format
nuc_dist.df <- ldply(slopes, ldply)
nuc_dist.df$group <- factor(1:4, labels=c("Silent", "G2", "G3", "Expressed"))
nuc_dist.df$celltype <- rep(factor(1:3, labels=c("mOSN", "GBC", "HBC")), each=4)
nuc_dist.df
```

```{r omp_ngn_icam_nuc_rna_range4_group1_and_4_peak_slopes_hbc_noOutlier, dev=c("png", "pdf"), fig.width=4, fig.height=6}
library(ggplot2)
theme_set(theme_bw())
gg <- ggplot(nuc_dist.df[nuc_dist.df$group=="Silent" | nuc_dist.df$group=="Expressed",], aes(celltype, index, fill=group))
gg <- gg + geom_bar(stat="identity", position="dodge") + facet_grid(.~group)
gg <- gg + theme(legend.position="none", axis.text.x=element_text(face="bold", color="black")) + labs(x="", y="Basepairs")
gg <- gg + scale_fill_manual(values=col2[2:1]) + coord_cartesian(ylim=c(0, 300))
gg
```