Omp-tTA X tetO-Tet3 ribominus-RNA analysis
========================================================


```{r}
opts_knit$set(verbose=T)
library(reshape2)
library(plyr)
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/features.R"))
```

Extract FPKM values from Cuffdiff output
```
cd <- read.delim("~/s2/data/rna/cuffdiff/omp_ott3_rmrna_rep12_masked_uq_comp_js/gene_exp.diff")
rna <- cd[,c("value_1", "value_2")]
```

Average entries with common gene names
```
library(plyr)
rna[,3] <- cd$gene
colnames(rna) <- c("omp", "ott3", "gene")
rna.s <- ddply(rna, .(gene), summarize, omp=mean(omp), ott3=mean(ott3), .progress="text")
rownames(rna.s) <- rna.s$gene
rna.s <- rna.s[,c(2,3)]
rna.1log2 <- colwise(function(x) log2(x+1))(rna.s)
rownames(rna.1log2) <- rownames(rna.s)
rna.1log2$ott3.omp <- with(rna.1log2, ott3-omp)
saveRDS(rna.1log2, file="~/s2/analysis/rna/rdata/omp_ott3_rmrna_rep12_masked_comp_js_1log2.rds")
```

```{r}
rna.1log2 <- readRDS("~/s2/analysis/rna/rdata/omp_ott3_rmrna_rep12_masked_comp_js_1log2.rds")
```

Scatter OMP and O/TT3 log2(FPKM+1).
```{r, fig.width=4, fig.height=4}
library(ggplot2)
gg <- ggplot(rna.1log2, aes(omp, ott3))
gg + geom_point(alpha=I(1/10)) + geom_abline(slope=1, intercept=0, linetype=2)
```

Scatter replicates
```{r}
rna <- read.delim("~/s2/data/rna/cuffdiff/omp_ott3_rmrna_rep12_masked_uq_comp_js/genes.read_group_tracking")
rna.fpkm <- dcast(rna, tracking_id~condition+replicate, value.var="FPKM")
rna.fpkm.1log2 <- numcolwise(onelog2)(rna.fpkm)
cor(rna.fpkm.1log2)
```

```{r omp_rmrna_rep12_masked_uq_comp_fpkm_scatter, fig.width=4, fig.height=4, dev=c("png", "pdf")}
gg <- ggplot(rna.fpkm.1log2, aes(q1_0, q1_1))
gg <- gg + geom_point(alpha=I(1/10)) + geom_abline(slope=1, intercept=0, color=2)
gg <- gg + labs(x="Control rmRNA rep1", y="Control rmRNA rep2")
gg
```

```{r ott3_rmrna_rep12_masked_uq_comp_fpkm_scatter, fig.width=4, fig.height=4, dev=c("png", "pdf")}
gg <- ggplot(rna.fpkm.1log2, aes(q2_0, q2_1))
gg <- gg + geom_point(alpha=I(1/10)) + geom_abline(slope=1, intercept=0, color=2)
gg <- gg + labs(x="Tet3-tg rmRNA rep1", y="Tet3-tg rmRNA rep2")
gg
```

### 5hmC heatmaps 
Load omp, o/tt3 hmc gene position matrices
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
omp.hmc.pos <- makeImage("omp_hmc_dampen5", "gene_whole_W200N50F50_chr",  data_type="rpkm_rep/mean", image=FALSE)
ott3.hmc.pos <- makeImage("ott3_hmc_dampen5", "gene_whole_W200N50F50_chr",  data_type="rpkm_rep/mean", image=FALSE)
ott3.omp.hmc.pos <- ott3.hmc.pos - omp.hmc.pos
```

Principal components analysis on gene body to order
```{r}
omp.hmc.pos.pc <- prcomp(omp.hmc.pos[,51:100])
ott3.hmc.pos.pc <- prcomp(ott3.hmc.pos[,51:100])
omp.hmc.pos.pred <- predict(omp.hmc.pos.pc, omp.hmc.pos[,51:100])
ott3.hmc.pos.pred <- predict(ott3.hmc.pos.pc, ott3.hmc.pos[,51:100])

omp.hmc.pos.pc1 <- omp.hmc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(omp.hmc.pos)),]
ott3.hmc.pos.pc1 <- ott3.hmc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(ott3.hmc.pos)),]
omp.hmc.pos.ott3.pc1 <- omp.hmc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,1]),]), rownames(omp.hmc.pos)),]
ott3.hmc.pos.omp.pc1 <- ott3.hmc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,1]),]), rownames(ott3.hmc.pos)),]

omp.hmc.pos.pc2 <- omp.hmc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,2]),]), rownames(omp.hmc.pos)),]
ott3.hmc.pos.pc2 <- ott3.hmc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,2]),]), rownames(ott3.hmc.pos)),]
omp.hmc.pos.ott3.pc2 <- omp.hmc.pos[match(rownames(ott3.hmc.pos.pred[order(ott3.hmc.pos.pred[,2]),]), rownames(omp.hmc.pos)),]
ott3.hmc.pos.omp.pc2 <- ott3.hmc.pos[match(rownames(omp.hmc.pos.pred[order(omp.hmc.pos.pred[,2]),]), rownames(ott3.hmc.pos)),]
```

Order difference matrix
```{r}
ott3.omp.hmc.pos.omp.pc1 <- na.omit(ott3.omp.hmc.pos[match(rownames(omp.hmc.pos.pc1), rownames(ott3.omp.hmc.pos)),])
ott3.omp.hmc.pos.ott3.pc1<- na.omit(ott3.omp.hmc.pos[match(rownames(ott3.hmc.pos.pc1), rownames(ott3.omp.hmc.pos)),])
```


Compare orders with RNA
```{r}
rna.1log2.omp.pc1 <- na.omit(rna.1log2[match(rownames(omp.hmc.pos.pc1), rownames(rna.1log2)),])
rna.1log2.ott3.pc1 <- na.omit(rna.1log2[match(rownames(ott3.hmc.pos.pc1), rownames(rna.1log2)),])

```

Group in 100 chunks
```{r}
source("~/src/seqAnalysis/R/boot.R")
ott3.omp.hmc.pos.omp.pc1.c100 <- foreach(c=isplitRows(ott3.omp.hmc.pos.omp.pc1[,51:100], chunks=100), .combine="rbind") %do% mean(c, na.rm=TRUE)
ott3.omp.hmc.pos.omp.pc1.c100 <- as.data.frame(ott3.omp.hmc.pos.omp.pc1.c100)
ott3.omp.hmc.pos.omp.pc1.c100$index <- 100:1
ott3.omp.hmc.pos.omp.pc1.c100.boot <- foreach(c=isplitRows(ott3.omp.hmc.pos.omp.pc1[,51:100], chunks=100), .combine="rbind") %do% bootCI(apply(c, 1, mean))
ott3.omp.hmc.pos.omp.pc1.c100 <- cbind(ott3.omp.hmc.pos.omp.pc1.c100, ott3.omp.hmc.pos.omp.pc1.c100.boot)
colnames(ott3.omp.hmc.pos.omp.pc1.c100)[3:4] <- c("ott3.omp.lower","ott3.omp.upper")

ott3.omp.hmc.pos.ott3.pc1.c100 <- foreach(c=isplitRows(ott3.omp.hmc.pos.ott3.pc1[,51:100], chunks=100), .combine="rbind") %do% mean(c, na.rm=TRUE)
ott3.omp.hmc.pos.ott3.pc1.c100 <- as.data.frame(ott3.omp.hmc.pos.ott3.pc1.c100)
ott3.omp.hmc.pos.ott3.pc1.c100$index <- 100:1
ott3.omp.hmc.pos.ott3.pc1.c100.boot <- foreach(c=isplitRows(ott3.omp.hmc.pos.ott3.pc1[,51:100], chunks=100), .combine="rbind") %do% bootCI(apply(c, 1, mean))
ott3.omp.hmc.pos.ott3.pc1.c100 <- cbind(ott3.omp.hmc.pos.ott3.pc1.c100, ott3.omp.hmc.pos.ott3.pc1.c100.boot)
colnames(ott3.omp.hmc.pos.ott3.pc1.c100)[3:4] <- c("ott3.omp.lower","ott3.omp.upper")

rna.1log2.omp.pc1.c100 <- foreach(c=isplitRows(rna.1log2.omp.pc1[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.omp.pc1.c100 <- as.data.frame(rna.1log2.omp.pc1.c100)
rna.1log2.omp.pc1.c100$index <- 100:1
rna.1log2.omp.pc1.c100.boot <- foreach(c=isplitRows(rna.1log2.omp.pc1[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, bootCI)
rna.1log2.omp.pc1.c100 <- cbind(rna.1log2.omp.pc1.c100, rna.1log2.omp.pc1.c100.boot[seq(1, nrow(rna.1log2.omp.pc1.c100.boot), 2),], rna.1log2.omp.pc1.c100.boot[seq(2, nrow(rna.1log2.omp.pc1.c100.boot), 2),])
colnames(rna.1log2.omp.pc1.c100)[5:10] <- c("omp.lower", "ott3.lower", "ott3.omp.lower", "omp.upper", "ott3.upper", "ott3.omp.upper")

rna.1log2.ott3.pc1.c100 <- foreach(c=isplitRows(rna.1log2.ott3.pc1[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.ott3.pc1.c100 <- as.data.frame(rna.1log2.ott3.pc1.c100)
rna.1log2.ott3.pc1.c100$index <- 100:1
rna.1log2.ott3.pc1.c100.boot <- foreach(c=isplitRows(rna.1log2.ott3.pc1[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, bootCI)
rna.1log2.ott3.pc1.c100 <- cbind(rna.1log2.ott3.pc1.c100, rna.1log2.ott3.pc1.c100.boot[seq(1, nrow(rna.1log2.ott3.pc1.c100.boot), 2),], rna.1log2.ott3.pc1.c100.boot[seq(2, nrow(rna.1log2.ott3.pc1.c100.boot), 2),])
colnames(rna.1log2.ott3.pc1.c100)[5:10] <- c("omp.lower", "ott3.lower", "ott3.omp.lower", "omp.upper", "ott3.upper", "ott3.omp.upper")
```

```{r}
rna.1log2.omp.pc1.c100$wilcox.FDR <- p.adjust(foreach(c=isplitRows(rna.1log2.omp.pc1[,1:3], chunks=100), .combine="rbind") %do% wilcox.test(c[,3])$p.value, method="fdr")
rna.1log2.omp.pc1.c100$wilcox.FDR.05 <- cut(rna.1log2.omp.pc1.c100$wilcox.FDR, breaks=c(0, .05, 1))
rna.1log2.ott3.pc1.c100$wilcox.FDR <- p.adjust(foreach(c=isplitRows(rna.1log2.ott3.pc1[,1:3], chunks=100), .combine="rbind") %do% wilcox.test(c[,3])$p.value, method="fdr")
rna.1log2.ott3.pc1.c100$wilcox.FDR.05 <- cut(rna.1log2.ott3.pc1.c100$wilcox.FDR, breaks=c(0, .05, 1))

```

#### Plot heatmaps - PC1
```{r "gene_whole_W200N50F50_omp_hmc_rep12_mean_ordered_by_gene_body_pc1", fig.height=6, fig.width=6,dev=c('png', 'pdf')}
MP.heat(omp.hmc.pos.pc1, range=c(0,1.5), average=50)
```

```{r "gene_whole_W200N50F50_ott3_hmc_rep12_mean_ordered_by_omp_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.hmc.pos.omp.pc1, range=c(0,1.5), average=50)
```

O/TT3 - OMP gene body 5hmC ordered by OMP 5hmC PC1
```{r "ott3_sub_omp_rep12_gene_body_hmc_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(ott3.omp.hmc.pos.omp.pc1.c100, aes(V1, index))
gg <- gg + geom_vline(xintercept=0, color="red")
gg <- gg  + geom_point(size=2) + xlab("log2(RPM)") + ylab("") + theme(legend.position="none", axis.text.y=element_blank()) + geom_errorbarh(aes(xmin=ott3.omp.lower, xmax=ott3.omp.upper), height=0, size=.1)
gg
```

OMP rmRNA ordered by OMP 5hmC PC1
```{r "omp_rmrna_1log2_ordered_by_omp_hmc_rep12_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.omp.pc1.c100, aes(omp, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4))
```

O/TT3 rmRNA ordered by OMP 5hmC PC1
```{r "ott3_rmrna_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.omp.pc1.c100, aes(ott3, index))
gg <- gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4))
gg
```

O/TT3 - OMP rmRNA ratio ordered by OMP 5hmC PC1
```{r "ott3_omp_rmrna_rep12_1log2_ordered_by_omp_hmc_gene_body_pc1_mean_chunks100_nosig", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
theme_set(theme_gray())
gg <- ggplot(as.data.frame(rna.1log2.omp.pc1.c100), aes(ott3.omp, index))
gg <- gg + geom_vline(xintercept=0, color="red")
gg <- gg + geom_point(size=2) + xlab("log2(FPKM + 1)") + ylab("") + theme(legend.position="none", axis.text.y=element_blank()) + geom_errorbarh(aes(xmin=ott3.omp.lower, xmax=ott3.omp.upper), height=0, size=0.1)
gg
```

```{r "gene_whole_W200N50F50_omp_hmc_rep12_mean_ordered_by_ott3_1_hmc_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(omp.hmc.pos.ott3.pc1, range=c(0,1.5), average=50)
```

```{r "gene_whole_W200N50F50_ott3_hmc_rep12_mean_ordered_by_gene_body_pc1", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.hmc.pos.pc1, range=c(0,1.5), average=50)
```

O/TT3 - OMP gene body 5hmC ordered by O/TT3 5hmC PC1
```{r "ott3_sub_omp_rep12_gene_body_hmc_1log2_ordered_by_ott3_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(ott3.omp.hmc.pos.ott3.pc1.c100, aes(V1, index))
gg <- gg + geom_vline(xintercept=0, color="red")
gg <- gg  + geom_point(size=2) + xlab("log2(RPM)") + ylab("") + theme(legend.position="none", axis.text.y=element_blank()) + geom_errorbarh(aes(xmin=ott3.omp.lower, xmax=ott3.omp.upper), height=0, size=.1)
gg
```

OMP rmRNA ordered by O/TT3 5hmC PC1
```{r "omp_rmrna_1log2_ordered_by_ott3_1_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(omp, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4)) + labs(title=c("OMP RNA by O/Tet3 PC1"))
```

O/TT3 rmRNA ordered by O/TT3 5hmC PC1
```{r "ott3_rmrna_1log2_ordered_by_ott3_1_hmc_gene_body_pc1_mean_chunks100", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(ott3, index))
gg + geom_point() + xlab("log2(FPKM + 1)") + ylab("") + theme(axis.text.y=element_blank()) + coord_cartesian(xlim=c(0,4)) + labs(title=c("O/Tet3 RNA by O/Tet3 PC1"))
```

Plot O/TT3 - OMP rmRNA ratio ordered by O/TT3 5hmC PC1
```{r "ott3_omp_rmrna_rep12_1log2_ordered_by_ott3_hmc_gene_body_pc1_mean_chunks100_nosig", fig.height=4, fig.width=2, dev=c('png', 'pdf')}
gg <- ggplot(rna.1log2.ott3.pc1.c100, aes(ott3.omp, index))
gg <- gg + geom_vline(xintercept=0, color="red")
gg <- gg  + geom_point(size=2) + xlab("log2(FPKM + 1)") + ylab("") + theme(legend.position="none", axis.text.y=element_blank()) + geom_errorbarh(aes(xmin=ott3.omp.lower, xmax=ott3.omp.upper), height=0, size=.1)
gg
```

#### Prep RNA - PC2

```{r}
rna.1log2.omp.pc2 <- na.omit(rna.1log2[match(rownames(omp.hmc.pos.pc2), rownames(rna.1log2)),])
rna.1log2.ott3.pc2 <- na.omit(rna.1log2[match(rownames(ott3.hmc.pos.pc2), rownames(rna.1log2)),])
rna.1log2.omp.pc2.c100 <- foreach(c=isplitRows(rna.1log2.omp.pc2[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.omp.pc2.c100 <- as.data.frame(rna.1log2.omp.pc2.c100)
rna.1log2.omp.pc2.c100$index <- 100:1
rna.1log2.omp.pc2.c100.boot <- foreach(c=isplitRows(rna.1log2.omp.pc2[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, bootCI)
rna.1log2.omp.pc2.c100 <- cbind(rna.1log2.omp.pc2.c100, rna.1log2.omp.pc2.c100.boot[seq(1, nrow(rna.1log2.omp.pc2.c100.boot), 2),], rna.1log2.omp.pc2.c100.boot[seq(2, nrow(rna.1log2.omp.pc2.c100.boot), 2),])
colnames(rna.1log2.omp.pc2.c100)[5:10] <- c("omp.lower", "ott3.lower", "ott3.omp.lower", "omp.upper", "ott3.upper", "ott3.omp.upper")

rna.1log2.ott3.pc2.c100 <- foreach(c=isplitRows(rna.1log2.ott3.pc2[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, mean, na.rm=TRUE)
rna.1log2.ott3.pc2.c100 <- as.data.frame(rna.1log2.ott3.pc2.c100)
rna.1log2.ott3.pc2.c100$index <- 100:1
rna.1log2.ott3.pc2.c100.boot <- foreach(c=isplitRows(rna.1log2.ott3.pc2[,c(1:3)], chunks=100), .combine="rbind") %do% apply(c, 2, bootCI)
rna.1log2.ott3.pc2.c100 <- cbind(rna.1log2.ott3.pc2.c100, rna.1log2.ott3.pc2.c100.boot[seq(1, nrow(rna.1log2.ott3.pc2.c100.boot), 2),], rna.1log2.ott3.pc2.c100.boot[seq(2, nrow(rna.1log2.ott3.pc2.c100.boot), 2),])
colnames(rna.1log2.ott3.pc2.c100)[5:10] <- c("omp.lower", "ott3.lower", "ott3.omp.lower", "omp.upper", "ott3.upper", "ott3.omp.upper")
```

#### Plot heatmaps - PC2

```{r "gene_whole_W200N50F50_omp_hmc_rep12_mean_ordered_by_gene_body_pc2", fig.height=6, fig.width=6,dev=c('png', 'pdf')}
MP.heat(omp.hmc.pos.pc2, range=c(0,1.5), average=50)
```

```{r "gene_whole_W200N50F50_ott3_hmc_rep12_mean_ordered_by_omp_hmc_gene_body_pc2", fig.height=6, fig.width=6, dev=c('png', 'pdf')}
MP.heat(ott3.hmc.pos.omp.pc2, range=c(0,1.5), average=50)
```

