H3K27ac dips - profiles
========================================================

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/profiles2.R"))
```

```{r}
makeProfile2.allSamp("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", data_type="rpkm/mean")
```

```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_d3xog_mc,  fig.width=12, fig.height=4, dev=c("png", "pdf")}
par(mfrow=c(1,3), mar=c(2,2,2,2))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "icam_mc_rep1_q30_rmdup_extend300_mean_icam_mc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, .9), lab="H3K27ac dip", wsize=100)
abline(h=.45, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "ngn_mc_rep1_q30_rmdup_extend300_mean_ngn_mc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, .9), lab="H3K27ac dip")
abline(h=.45, lty=2)
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_mc", data_type="rpkm/mean",   cols=col3, y.vals=c(0, .9), lab="H3K27ac dip")
abline(h=.45, lty=2)
```


### 5hmC
Reduction of levels flanking H3K27ac dip site, however not complete loss. Explained by reduction of Dnmt3a-mediated 5mC substrate; however, targeting still occurs. 
Targeting of oxidation is Dnmt3a-independent.
```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_d3xog_hmc, fig.width=12, fig.height=4, dev=c("png", "pdf")}
par(mfrow=c(1,3), mar=c(2,2,2,2))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "icam_hmc_rep1_q30_rmdup_extend300_mean_icam_hmc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, 1.5), lab="H3K27ac dip")
abline(h=.45, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "ngn_hmc_rep1_q30_rmdup_extend300_mean_ngn_hmc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, 1.5), lab="H3K27ac dip")
abline(h=.45, lty=2)
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_hmc", data_type="rpkm/mean",   cols=col3, y.vals=c(0, 1.5), lab="H3K27ac dip")
abline(h=.45, lty=2)
```

#### O/Tet3
Overexpression of Tet3 targets H3K27ac dip flanking regions. Full oxidation
```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_omp_ott3, fig.width=4, fig.height=4, dev=c("png", "pdf")}
par(mfrow=c(1,1))
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "tt3_rep", data_type="rpkm/mean",   cols=col2, y.vals=c(0, 1.5), lab="H3K27ac dip")
```

#### Nucleosomes
Nucleosome depletion and structuring still occurs
```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_d3xog_nuc, fig.width=4, fig.height=4, dev=c("png", "pdf")}
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_nuc", data_type="rpkm/mean",   cols=col2, y.vals=c(.2, .6), baseline=T)
```

```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_d3xog_nuc_cells, fig.width=12, fig.height=4, dev=c("png", "pdf")}
par(mfrow=c(1,4), mar=c(2,2,2,2))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "icam_nuc_01234", data_type="rpkm/mean",   cols=col2[1], y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "ngn_nuc_456", data_type="rpkm/mean",   cols=col2[1], y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "omp_nuc_0123", data_type="rpkm/mean",   cols=col2[1], y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_nuc", data_type="rpkm/mean",   cols=col2, y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)
```


```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_d3xog_nuc_cells2, fig.width=8, fig.height=4, dev=c("png", "pdf")}
par(mfrow=c(1,3), mar=c(2,2,2,2))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "icam_nuc_01234", data_type="rpkm/mean",   cols=col2[1], y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "ngn_nuc_456", data_type="rpkm/mean",   cols=col2[1], y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)

plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_nuc", data_type="rpkm/mean",   cols=col2, y.vals=c(.2, .6), lab="H3K27ac dip")
abline(h=.4, lty=2)
```


#### Enhancer modifications
```{r}
par(mfrow=c(1,2))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr","moe_h3k4me1_rmdup_sub_moe_d3a_wt_input_q30_rmdup_smooth5", data_type="rpkm/mean",   y.vals=c(0, 5))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr","moe_h3k27ac_rmdup_sub_moe_d3a_wt_input_q30_rmdup_smooth5", data_type="rpkm/mean",   y.vals=c(0, 5))
```

### Combined
```{r ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W25F200_combined, fig.width=8, fig.height=8, dev=c("png", "pdf")}
par(mfrow=c(3,3), mar=c(2,2,2,2))
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "icam_mc_rep1_q30_rmdup_extend300_mean_icam_mc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, .9), lab="H3K27ac dip")
abline(h=.45, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "ngn_mc_rep1_q30_rmdup_extend300_mean_ngn_mc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, .9), lab="H3K27ac dip")
abline(h=.45, lty=2)
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_mc", data_type="rpkm/mean",   cols=col3, y.vals=c(0, .9), lab="H3K27ac dip")
abline(h=.45, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "icam_hmc_rep1_q30_rmdup_extend300_mean_icam_hmc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, 1.2), lab="H3K27ac dip")
abline(h=.6, lty=2)
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", 
      "ngn_hmc_rep1_q30_rmdup_extend300_mean_ngn_hmc_rep2_q30_rmdup", data_type="rpkm/mean",   cols=col3[1], y.vals=c(0, 1.2), lab="H3K27ac dip")
abline(h=.6, lty=2)
plot2.several("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr", "d3xog_hmc", data_type="rpkm/mean",   cols=col3, y.vals=c(0, 1.2), lab="H3K27ac dip")
abline(h=.6, lty=2)

plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr","moe_h3k4me1_rmdup_sub_moe_d3a_wt_input_q30_rmdup_smooth5", data_type="rpkm/mean",   y.vals=c(0, 5), lab="H3K27ac dip")
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr","moe_h3k27ac_rmdup_sub_moe_d3a_wt_input_q30_rmdup_smooth5", data_type="rpkm/mean",   y.vals=c(0, 5), lab="H3K27ac dip")
plot2("ak27_F3_interV_genes_W25F100_ak27_height3_min1.bed_W100F100_both_chr","d3a_het_dnase_sort_q30", data_type="rpkm/mean",   y.vals=c(0, 3), lab="H3K27ac dip")
```