D3a Rad21 sites
========================================================

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/profiles2.R"))
opts_chunk$set(warning=FALSE, message=FALSE, error=FALSE, results='hide')
```

#### Random sample of Rad21 sites
```{r, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr", data_type="bam_extend/mean_chrom_mean_0", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr", data_type="bam_ends/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr", data_type="rpkm/mean", rm.outliers=0.01)
```

#### Random sample of Rad21 sites, 100kb view
```{r, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr", data_type="bam_extend/mean_chrom_mean_0", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr", data_type="bam_extend/mean_chrom_mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr", data_type="bam_ends/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr", data_type="rpkm/mean", rm.outliers=0.01)
```

#### Rad21 sites, no CTCF, 50 kb view
```{r}
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr", data_type="bam_extend/mean_chrom_mean_0", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr", data_type="bam_ends/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr", data_type="rpkm/mean", rm.outliers=0.01)
```

```{r}
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr", data_type="bam_extend/mean_chrom_mean_0", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr", data_type="bam_extend/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr", data_type="bam_ends/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr", data_type="rpkm/mean", rm.outliers=0.01)

```

#### CTCF sites, no Rad21
```{r}
makeProfile2.allSamp("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr", data_type="bam_extend/mean_chrom_mean_0", rm.outliers=0.01)
#makeProfile2.allSamp("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr", data_type="bam_extend/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr", data_type="bam_ends/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr", data_type="rpkm/mean", rm.outliers=0.01)
```

#### Random sample of Rad21 sites, position randomized
```{r, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", data_type="bam_extend/mean_chrom_mean_0", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", data_type="bam_ends/mean", rm.outliers=0.01)
makeProfile2.allSamp("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", data_type="rpkm/mean", rm.outliers=0.01)
```

### 5hmC
#### Rad21, random sample and randomized positions
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,2), mar=c(2,2,2,2))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1))
plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1))
```

#### Rad21, random sample 100 kb view
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,1), mar=c(2,2,2,2))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1), range=c(251, 750))
#plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1))
```

#### Rad21 sites, no CTCF, 50 kb view
```{r}
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1), baseline=T, wsize=200)
```

#### Rad21 sites, no CTCF/DNase, 50 kb view
```{r}
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1), baseline=T, wsize=200)
```

#### CTCF sites, no Rad21
```{r}
plot2.several("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr", "d3a_hmc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1), baseline=F, wsize=200)
```

### 5mC
#### Rad21, random sample and randomized positions
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,2), mar=c(2,2,2,2))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(0, .6))
plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(0, .6))
```

#### Rad21, random sample 100 kb view
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,1), mar=c(2,2,2,2))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(0, .6), range=c(251, 750), wsize=200)
#plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(0, .6))
```

#### Rad21 sites, no CTCF, 50 kb view
```{r}
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(0, .6), wsize=200)
```

#### Rad21 sites, no CTCF/DNase, 50 kb view
```{r}
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(0, .6), wsize=200)
```

#### CTCF sites, no Rad21
```{r}
plot2.several("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr", "d3a_mc", data_type="rpkm/mean", group2="trim0.01", cols=col2, y.vals=c(.2, 1), baseline=F, wsize=200)
```

### Nucleosomes
#### Rad21, random sample and randomized positions, mean chrom mean 0
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,2),  mar=c(2,2,2,2))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(.8, 1.3), baseline=F)
plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(.8, 1.3), baseline=F)
```

#### Rad21, random sample 100 kb view, mean chrom mean 0
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,1),  mar=c(2,2,2,2))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(.8, 1.3), baseline=F, wsize=200, range=c(251, 750))
#plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(.8, 1.3), baseline=F)
```

#### Rad21, random sample 100 kb view, mean chrom mean 
```{r}
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean", group2="trim0.01", cols=col2, y.vals=c(.8, 1.3), baseline=F, wsize=200, range=c(401, 600))
abline(h=1, lty=2)
```

#### Rad21, RPKM - midpoints
```{r, fig.width=8, fig.height=4}
par(mfrow=c(1,2))
#plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W25F200_both_chr","d3a_nuc2", data_type="rpkm/mean", group2="trim0.01", cols=col2, baseline=F, y.vals=c(0, .5))
plot2.several("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr","d3a_nuc2", data_type="rpkm/mean", group2="trim0.01", cols=col2, baseline=T, wsize=200)
plot2.several("cad_n2a_rad21_r12_rand10E4_shuffle_nosex.bed_W25F200_both_chr","d3a_nuc2", data_type="rpkm/mean", group2="trim0.01", cols=col2, baseline=T, y.vals=c(0, .5))

```

#### Rad21 sites, no CTCF, 50 kb view, mean chrom mean 0
```{r}
par(mfrow=c(1,1))
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(1, 1.4), baseline=T, wsize=200, range=c(201, 300))
par(mfrow=c(1,1))
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr","d3a_nuc2", data_type="rpkm/mean", group2="trim0.01", cols=col2, baseline=F, wsize=200)
```

#### Rad21 sites, no CTCF/DNase, 50 kb view, mean chrom mean 0
```{r}
par(mfrow=c(1,1))
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(1, 1.4), baseline=T, wsize=200, range=c(201, 300))
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr","d3a_nuc_extend_sub", data_type="bam_extend/mean", group2="trim0.01", cols=col2, baseline=F, wsize=200, range=c(201, 300))
plot2.several("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr","d3a_nuc2", data_type="rpkm/mean", group2="trim0.01", cols=col2, baseline=F, wsize=200)
```

#### CTCF sites, no Rad21
```{r}
plot2.several("cad_n2a_ctcf_r12_sub_cad_n2a_rad21_r12_nosex.bed_W200F250_both_chr","d3a_nuc_extend", data_type="bam_extend/mean_chrom_mean_0", group2="trim0.01", cols=col2, y.vals=c(1, 1.4), baseline=T, wsize=200, range=c(201, 300))
```

### DNase

#### Rad21, random sample 100 kb view
```{r}
plot2("cad_n2a_rad21_r12_rand10E4_nosex.bed_W200F500_both_chr","d3a_het_dnase_sort_q30", data_type="bam_ends/mean", group2="trim0.01", wsize=200)
```

#### Rad21 sites, no CTCF, 50 kb view
```{r}
plot2("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr","d3a_het_dnase_sort_q30", data_type="bam_ends/mean", group2="trim0.01", wsize=200)
```

```{r}
plot2("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex.bed_W200F250_both_chr","d3a_het_dnase_sort_q30", data_type="bam_ends/mean", group2="trim0.01", wsize=200)
```

#### CTCF sites, no Rad21
```{r}
plot2("cad_n2a_rad21_r12_sub_cad_n2a_ctcf_r12_nosex_sub_d3a_het_dnase_sort_q30_dnase.bed_W200F250_both_chr","d3a_het_dnase_sort_q30", data_type="bam_ends/mean", group2="trim0.01", wsize=200)
```
