D3xOG rmRNA analysis -- Repeats
========================================================

What percentage of reads map to repeats?
What classes of repeats are transcribed?
How do the expression levels of these classes change in Dnmt3a KOs?

Associate reads with repeats using both Cuffdiff and HTSeq-count

```{r}
suppressPackageStartupMessages(library(DESeq))
library(ggplot2)
```

```{r}
input <- data.frame(c("wt", "ko"), c("d3xog_wt_rmrna_blank_rmsk_count_nh20", "d3xog_ko_rmrna_blank_rmsk_count_nh20"), c("wt", "ko"))
cds <- newCountDataSetFromHTSeqCount(input, "~/s2/data/rna/htseq/")
cds <- estimateSizeFactors(cds)
cds <- estimateDispersions(cds, method="blind", sharingMode="fit-only")
cds.counts <- counts(cds, normalized=T)
```

```{r}
ht.wt <- read.delim("~/s2/data/rna/htseq/d3xog_wt_rmrna_blank_rmsk_count_nh20", header=FALSE)
ht.ko <- read.delim("~/s2/data/rna/htseq/d3xog_ko_rmrna_blank_rmsk_count_nh20", header=FALSE)

ht.wt.no <- ht.wt[grep("no_feature", ht.wt[,1]),]
ht.ko.no <- ht.ko[grep("no_feature", ht.wt[,1]),]

# Percent reads mapped to repeats
(sum(ht.wt[,2]) - ht.wt.no[,2]) / sum(ht.wt[,2])
(sum(ht.ko[,2]) - ht.ko.no[,2]) / sum(ht.ko[,2])

# Percent reads mapped to repeats, no rRNA/tRNA
ht.wt.nrt <-ht.wt[-grep("rRNA|tRNA", ht.wt[,1]),]
ht.ko.nrt <-ht.ko[-grep("rRNA|tRNA", ht.ko[,1]),]

(sum(ht.wt.nrt[,2]) - ht.wt.no[,2]) / sum(ht.wt.nrt[,2])
(sum(ht.ko.nrt[,2]) - ht.ko.no[,2]) / sum(ht.ko.nrt[,2])
```

*More reads mapping to repeats in KO than WT*

```{r}
cds.counts <- log2(cds.counts+1)
cds.counts <- as.data.frame(cds.counts)
cds.counts$ko.wt <- with(cds.counts, ko-wt)
```

```{r}
gg <- ggplot(cds.counts, aes(wt, ko))
gg + geom_point(alpha=I(1/5)) + geom_abline(slope=1, xintercept=0, color="red")

```

#### Annotate snRNAs and tRNA
```{r}
cds.counts$rna.class <- "NONE"
cds.counts$rna.class[grep("^U", rownames(cds.counts))] <- "snRNA"
cds.counts$rna.class[grep("tRNA", rownames(cds.counts))] <- "tRNA"
```

```{r}
gg <- ggplot(cds.counts, aes(wt, ko, color=rna.class))
gg + geom_point(alpha=I(1/5)) + geom_abline(slope=1, xintercept=0, color="red") + scale_color_manual(values=c("black", "red", "blue")) + theme(legend.position=c(.75, .25))
```

#### Aggregate by class
```{r}
rmsk2 <- read.delim("~/lib/features_general/rmsk2.bed", header=FALSE, colClasses=c("character", "numeric", "numeric", "character", "character", "character"))
cds.counts$class <- rmsk2[match(rownames(cds.counts), rmsk2[,4]),5]
cds.counts.class <- ddply(cds.counts, .(class), function(d) apply(d[,1:3], 2, median))
```

```{r}
gg <- ggplot(cds.counts.class, aes(wt, ko))
gg + geom_point() + geom_abline(slope=1, xintercept=0, color="red")
```

```{r}
cds.counts.class$class <- factor(cds.counts.class$class, levels=cds.counts.class$class[order(cds.counts.class$ko.wt)])
theme_set(theme_bw())
gg <- ggplot(cds.counts.class, aes(class, ko.wt))
gg <- gg + geom_bar(stat="identity")
gg <- gg + labs(x="", y="log2(KO / WT + 1) Normalized reads")
gg <- gg + theme(axis.text.x=element_text(face="bold"))
gg
```

*Housekeeping, or functional, repeats seem to be upregulated*


### 5mC/5hmC of snRNAs 

```
rmsk <- read.delim("~/s2/analysis/features/norm/rpkm/mean/summaries/d3a_bt2_rmsk2.bed_chr_sqrt", row.names=NULL)
rmsk2 <- read.delim("~/lib/features_general/rmsk2.bed", header=F)
m <- match(rmsk[,1], rmsk2[,4])
rmsk <- as.data.frame(rmsk)
rmsk$class <- rmsk2[m, 5]
saveRDS(rmsk, file="~/s2/analysis/features/norm/rpkm/mean/rdata/d3a_bt2_rmsk2.bed_sqrt_class.rds")
```

```{r}
rmsk <- readRDS("~/s2/analysis/features/norm/rpkm/mean/rdata/d3a_bt2_rmsk2.bed_sqrt_class.rds")

# Remove high-valued outliers
q <- min(apply(rmsk[,2:5], 2, quantile, c(.99)))

rmsk <- rmsk[apply(rmsk[,2:5], 1, max) <= q,]

rmsk.class <- ddply(rmsk, .(class), function(d) apply(d[,2:5], 2, median))
rmsk.class.m <- melt(rmsk.class)
```


```{r}
#gg <- ggplot(rmsk.class.m, aes(variable, value))
#gg + geom_bar(stat="identity") + facet_wrap(~class)
```

```{r}
rmsk.ratio <- data.frame(rmsk$row.names, rmsk$class, hmc.ko.wt=computeScoreRatios(rmsk$moe_d3a_ko_hmc_bt2_rpkm, rmsk$moe_d3a_wt_hmc_bt2_rpkm), mc.ko.wt=computeScoreRatios(rmsk$moe_d3a_ko_mc_bt2_rpkm, rmsk$moe_d3a_wt_mc_bt2_rpkm))
rmsk.ratio.class <- ddply(rmsk.ratio, .(rmsk.class), function(d) apply(d[,3:4], 2, mean))
rmsk.ratio.class.m <- melt(rmsk.ratio.class)
#rmsk.ratio.class.m$rmsk.class <- factor(rmsk.ratio.class.m$rmsk.class, levels=levels(rmsk.ratio.class.m)[order(rmsk.ratio.class.m$value[rmsk.ratio.class.m$variable=="hmc.ko.wt"])])
```


```{r}
gg <- ggplot(rmsk.ratio.class.m, aes(rmsk.class, value))
gg + geom_bar(stat="identity") + facet_wrap(~variable) + coord_cartesian(ylim=c(-1, 1))
```

#### With htseq count output

```{r}
input <- data.frame(c("wt_hmc", "ko_hmc", "wt_mc", "ko_mc"), c("moe_d3a_wt_hmc_sort_bt2_rmsk_counts_nh20", "moe_d3a_ko_hmc_sort_bt2_rmsk_counts_nh20", "moe_d3a_wt_mc_sort_bt2_rmsk_counts_nh20", "moe_d3a_ko_mc_sort_bt2_rmsk_counts_nh20"), c("wt_hmc", "ko_hmc", "wt_mc", "ko_mc"))
dna.cds <- newCountDataSetFromHTSeqCount(input, "~/s2/analysis/htseq/")
dna.cds <- estimateSizeFactors(dna.cds)
dna.counts <- counts(dna.cds, normalized=T)
dna.counts <- data.frame(log2(dna.counts + 1))
```

```{r}
gg <- ggplot(dna.counts, aes(wt_hmc, ko_hmc))
gg + geom_point()
```

```{r}
gg <- ggplot(dna.counts, aes(wt_mc, ko_mc))
gg + geom_point()
```

```{r}
dna.counts <- transform(dna.counts, hmc.ko.wt=ko_hmc - wt_hmc, mc.ko.wt=ko_mc - wt_mc)
```

```{r}
dna.counts$class <- rmsk2[match(rownames(dna.counts), rmsk2[,4]),5]
dna.counts.class <- ddply(dna.counts, .(class), function(d) apply(d[,1:6], 2, median))
```

```{r}
gg <- ggplot(dna.counts.class, aes(wt_hmc, ko_hmc))
gg + geom_point() + geom_abline(slope=1, xintercept=0, color="red")
```

```{r}
dna.counts.class$class <- factor(dna.counts.class$class, levels=dna.counts.class$class[order(dna.counts.class$mc.ko.wt)])
theme_set(theme_bw())
gg <- ggplot(dna.counts.class, aes(class, mc.ko.wt))
gg <- gg + geom_bar(stat="identity")
gg <- gg + labs(x="", y="log2(KO / WT + 1) Normalized reads")
gg <- gg + theme(axis.text.x=element_text(face="bold"))
gg
```

Combine RNA and DNA modifications
```{r}
both.counts.class <- data.frame(cds.counts.class, dna.counts.class)
both.counts.class <- both.counts.class[,-5]
colnames(both.counts.class) <- c("class", "rna.wt", "rna.ko", "rna.ko.wt", "hmc.wt", "hmc.ko", "mc.wt", "mc.ko", "hmc.ko.wt", "mc.ko.wt")
```

```{r}
gg <- ggplot(both.counts.class, aes(hmc.ko.wt, rna.ko.wt))
gg + geom_point() + coord_cartesian(xlim=c(-.4, .4))
```

```{r}
gg <- ggplot(both.counts.class, aes(mc.ko.wt, rna.ko.wt))
gg + geom_point() + coord_cartesian(xlim=c(-.4, .4))
```
### Expression of adjacent loci
### genomic plot


