5hmC/5mC/mRNA strand asymmetry
========================================================

Gene profiles
--------------------------------------------------------
### Difference 

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/profiles2.R"))
```

### First try with full data set, do not remove outliers
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
```
#### OMP 5hmC Coding - Template
```{r}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean", cols=col4_mod, wsize=200, fname="manual", y.vals=c(-.3, .2))
```
#### Neurog 5hmC Coding - Template
```{r}
plot2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean", cols=col4_mod, wsize=200, fname="manual", y.vals=c(-.3, .2))
```

#### Icam 5hmC Coding - Template
```{r}
plot2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean", cols=col4_mod, wsize=200, fname="manual", y.vals=c(-.3, .2))
```

### Top/bottom 2% removed at each position, split by deciles, plot 20% and 100%
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_deciles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_deciles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_deciles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_deciles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_deciles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_deciles", data_type="strand_diff/mean", rm.outliers=0.02)
```
#### OMP 5hmC Coding - Template
```{r omp_hmc_diff_deciles, fig.width=9, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_deciles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,8), y.vals=c(-.2, .1), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```
#### Neurog 5hmC Coding - Template
```{r ngn_hmc_diff_deciles, fig.width=9, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_deciles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,8), y.vals=c(-.2, .1), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```

#### Icam 5hmC Coding - Template
```{r icam_hmc_diff_deciles, fig.width=9, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_deciles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,8), y.vals=c(-.2, .1), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```

#### OMP 5mC Coding - Template
```{r omp_mc_diff_deciles, fig.width=9, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_deciles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,8), y.vals=c(-.3, .2), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```
#### Neurog 5mC Coding - Template
```{r ngn_mc_diff_deciles, fig.width=9, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_deciles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,8), y.vals=c(-.2, .1), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```

#### Icam 5mC Coding - Template
```{r icam_mc_diff_deciles, fig.width=9, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_deciles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,8), y.vals=c(-.3, .2), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```
### Fraction

### Top/bottom 2% removed at each position
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
```

#### OMP 5hmC (Coding - Template)/Total
```{r, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(1,4)], wsize=200, fname="manual", group2_col=c(1,4), y.vals=c(.3, .7))
abline(h=0.5, lty=2)
```
#### Neurog 5hmC (Coding - Template)/Total
```{r, dev='pdf'}
plot2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(1,4)], wsize=200, fname="manual", group2_col=c(1,4), y.vals=c(.3, .7))
abline(h=0.5, lty=2)
```

#### Icam 5hmC (Coding - Template)/Total
```{r}
#plot2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(1,4)], wsize=200, fname="manual", group2_col=c(1,4), y.vals=c(.3, .7))
```

Quantification by gene flank and body
--------------------------------------------------------

Construct position matrices for each cell type divided into expression quartiles
```
positionMatrix.group("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
positionMatrix.group("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
positionMatrix.group("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
```
Load 5hmC matrices and compute mean flank and mid values
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/strand2.R"))
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/ggplot.R"))
hmc.list <- lapply(c("omp", "ngn", "icam"), function(ct) lapply(c(0,2,3,4), function(x) read.delim(paste("~/s2/analysis/profiles/norm/strand_diff/mean/gene_whole_W200N50F50_chr/images/",ct,"_hmc_120424_rmdup_plus_", ct, "_hmc_120424_rmdup_minus_W100_S25_", ct, "_quartiles_", x, sep=""), header=F, row.names=1)))
for(i in 1:length(hmc.list)) {names(hmc.list[[i]]) <- c("0", "2", "3", "4")}
hmc.list.df <- lapply(hmc.list, compute_mean_gene_set)
names(hmc.list.df) <- c("omp", "ngn", "icam")
hmc.list.df2 <- ldply(hmc.list.df)

hmc.list.df2[,2] <- as.factor(hmc.list.df2[,2])
levels(hmc.list.df2[,2]) <-c("0-25%", "25-50%", "50-75%", "75-100%")
hmc.fac <- factor(1:3, labels=c("omp", "ngn", "icam"))
hmc.list.df2[,1] <- hmc.fac[match(as.character(hmc.list.df2[,1]), as.character(hmc.fac))]
levels(hmc.list.df2[,1]) <- c("mOSN", "GBC", "HBC")
```

Plot mean value, split by grouping
```{r omp_ngn_icam_hmc_strand_diff_flank_body, dev='pdf', fig.height=6, fig.width=4.5}
theme_set(theme_bw())
hmc.list.gg <- ggplot(hmc.list.df2, aes(pos, val, fill=.id, color=.id))
hmc.list.gg <- hmc.list.gg + stat_summary(geom="bar", fun.y="mean") + stat_sum_df("mean_cl_normal", geom="errorbar") + facet_grid(.id~group) + scale_fill_grey() + scale_color_grey() 
hmc.list.gg <- hmc.list.gg + theme(legend.position="none") + ylab("Coding - Template 5hmC") + xlab("")
hmc.list.gg

```

Wilcoxon p-values for Body/Flank comparisons
```{r}
sapply(levels(hmc.list.df2$.id), function(ct) sapply(levels(hmc.list.df2$group), function(x) with(hmc.list.df2[hmc.list.df2$.id==ct & hmc.list.df2$group==x,], wilcox.test(val[pos=="Body"], val[pos=="Flank"])$p.value)))

  ```
Repeat for 5mC data.
Construct position matrices for each cell type divided into expression quartiles
```
positionMatrix.group("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
positionMatrix.group("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
positionMatrix.group("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
```
Load 5hC matrices and compute mean flank and mid values
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/strand2.R"))
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/ggplot.R"))
mc.list <- lapply(c("omp", "ngn", "icam"), function(ct) lapply(c(0,2,3,4), function(x) read.delim(paste("~/s2/analysis/profiles/norm/strand_diff/mean/gene_whole_W200N50F50_chr/images/",ct,"_mc_rmdup_plus_", ct, "_mc_rmdup_minus_W100_S25_", ct, "_quartiles_", x, sep=""), header=F, row.names=1)))
for(i in 1:length(mc.list)) {names(mc.list[[i]]) <- c("0", "2", "3", "4")}

mc.list.df <- lapply(mc.list, compute_mean_gene_set)
names(mc.list.df) <- c("omp", "ngn", "icam")
mc.list.df2 <- ldply(mc.list.df)

mc.list.df2[,2] <- as.factor(mc.list.df2[,2])
levels(mc.list.df2[,2]) <-c("0-25%", "25-50%", "50-75%", "75-100%")
mc.fac <- factor(1:3, labels=c("omp", "ngn", "icam"))
mc.list.df2[,1] <- mc.fac[match(as.character(mc.list.df2[,1]), as.character(mc.fac))]
levels(mc.list.df2[,1]) <- c("mOSN", "GBC", "HBC")
```

Plot mean value, split by grouping
```{r omp_ngn_icam_mc_strand_diff_flank_body, dev='pdf', fig.height=6, fig.width=4.5}
theme_set(theme_bw())
mc.list.gg <- ggplot(mc.list.df2, aes(pos, val, fill=.id, color=.id))
mc.list.gg <- mc.list.gg + stat_summary(geom="bar", fun.y="mean") + stat_sum_df("mean_cl_normal", geom="errorbar") + facet_grid(.id~group) + scale_fill_grey() + scale_color_grey() 
mc.list.gg <- mc.list.gg + theme(legend.position="none") + ylab("Coding - Template 5mC") + xlab("")
mc.list.gg

```

Wilcoxon p-values for Body/Flank comparisons
```{r}
sapply(levels(mc.list.df2$.id), function(ct) sapply(levels(mc.list.df2$group), function(x) with(mc.list.df2[mc.list.df2$.id==ct & mc.list.df2$group==x,], wilcox.test(val[pos=="Body"], val[pos=="Flank"])$p.value)))

```
TSS Heatmaps
--------------------------------------------------------
Matrix of plus/minus strand differences for a given sample. For genes, plus/minus strand designation adjusted as coding/template strand.
First order MOE Dnmt3a WT polyA-RNA-seq by coding/template difference within the region -5 kb to 1.25 kb upstream of the TSS.

To make TSS RNA difference matrix, In terminal while in omp_rmrna dir,


```
$ bamStrand.py -o ~/s2/data/omp_rmrna_strand_25.trk -w 25 --paired-end omp_rmrna.bam
$ group.py -t omp_rmrna_strand_25
```

```{r}
positionMatrix.all("refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="bam/mean")
omp.rmrna <- makeImage("omp_rmrna", "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="bam/mean", image=FALSE)
omp.rmrna
```


```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
moe.rna <- read.delim("~/s2/analysis/profiles/norm/strand_diff/mean/refGene_noRandom_order_outsides2_tss_W25F200_chr/images/moe_d3a_wt_mrna_plus_sub_minus_1log_na_omit", header=T)
moe.rna.up.mean <- apply(moe.rna[,1:150], 1, mean)
moe.rna.up.mean <- sort(moe.rna.up.mean)
```

Order original matrix by these values and plot to check. Plot saved to "refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_moe_d3a_wt_mrna_plus_sub_minus_1log_na_omit_order_-5kbTo-1250bp.pdf"

```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_moe_d3a_wt_mrna_plus_sub_minus_1log_na_omit_order_m5kbTom1250bp, dev='pdf'}
moe.rna.ord.moe.rna.up <- moe.rna[match(names(moe.rna.up.mean), rownames(moe.rna)),]
MP.heat(as.matrix(moe.rna.ord.moe.rna.up), range=c(-.02, .02), average=50)

```


Order MOE Dnmt3a WT 5hmC matrix by RNA coding/template difference. Plot in "refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_moe_d3a_wt_hmc_plus_sub_minus_order_m5kbTom1250bp.pdf"

```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_moe_d3a_wt_hmc_plus_sub_minus_order_m5kbTom1250bp, dev='pdf'}
moe.hmc <- makeImage("moe_d3a_wt_hmc_plus_sub_minus", "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE)
moe.hmc.ord.moe.rna.up <- moe.hmc[match(names(moe.rna.up.mean), rownames(moe.hmc)),]
MP.heat(as.matrix(moe.hmc.ord.moe.rna.up), range=c(-.005, .005), average=100)

```

Repeat with developmental celltype data. First construct difference matrices. 

```
positionMatrix.all(anno="refGene_noRandom_order_outsides2_tss_W25F200_chr", "strand_diff/mean")

```

Test OMP 5hmC dataset. Heatmap saved in "refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25_order_m5kbTom1250bp.pdf"

#### OMP 5hmC Coding - Template
```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25_order_m5kbTom1250bp, dev='pdf'}
omp.hmc <- makeImage("omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE)
omp.hmc.ord.moe.rna.up <- omp.hmc[match(names(moe.rna.up.mean), rownames(omp.hmc)),]
MP.heat(as.matrix(omp.hmc.ord.moe.rna.up), range=c(-.25, .25), average=100)

```

Repeat with other sets
```{r}
pos.hmc <- lapply(c("omp", "ngn", "icam"), function(x) makeImage(paste(x, "hmc_120424_rmdup_plus", x, "hmc_120424_rmdup_minus_W100_S25", sep="_"), "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE))
pos.hmc.ord <- lapply(pos.hmc, function(x) x[match(names(moe.rna.up.mean), rownames(x)),])
pos.mc <- lapply(c("omp", "ngn", "icam"), function(x) makeImage(paste(x, "mc_rmdup_plus", x, "mc_rmdup_minus_W100_S25", sep="_"), "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE))
pos.mc.ord <- lapply(pos.mc, function(x) x[match(names(moe.rna.up.mean), rownames(x)),])
```

#### Neurog1 5hmC Coding - Template
```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25_order_m5kbTom1250bp, dev='pdf'}
MP.heat(as.matrix(pos.hmc.ord[[2]]), range=c(-.25, .25), average=100)
```

#### Icam 5hmC Coding - Template
```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25_order_m5kbTom1250bp, dev='pdf'}
MP.heat(as.matrix(pos.hmc.ord[[3]]), range=c(-.25, .25), average=100)
```

#### OMP 5mC Coding - Template
```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25_order_m5kbTom1250bp, dev='pdf'}
MP.heat(as.matrix(pos.mc.ord[[1]]), range=c(-.25, .25), average=100)
```

#### Neurog 5mC Coding - Template
```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25_order_m5kbTom1250bp, dev='pdf'}
MP.heat(as.matrix(pos.mc.ord[[2]]), range=c(-.25, .25), average=100)
```

#### Icam 5mC Coding - Template
```{r refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25_order_m5kbTom1250bp, dev='pdf'}
MP.heat(as.matrix(pos.mc.ord[[3]]), range=c(-.25, .25), average=100)
```

