5hmC/5mC/mRNA strand asymmetry
========================================================


Load source files
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/strand2.R"))
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/ggplot.R"))
```

Gene profiles
--------------------------------------------------------
### Difference 

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/profiles2.R"))
```


### Top/bottom 2% removed at each position, split by deciles, plot 20% and 100%
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
```
#### OMP 5hmC Coding - Template
```{r gene_whole_W200N50F50_omp_hmc_120424_rmdup_diff_quartile4, fig.width=9, dev=c('png', 'pdf')}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(4)], wsize=200, fname="manual", group2_col=c(4), y.vals=c(-.2, .1), lab=c("TSS", "TES"))
abline(h=0, lty=2)
```


Fraction
--------------

### Quartiles
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
```

#### OMP 5hmC (Coding - Template)/Total
```{r "gene_whole_W200N50F50_omp_hmc_120424_rmdup_fraction_quartile4", fig.width=9, dev=c('png','pdf')}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(4)], wsize=200, fname="manual", group2_col=c(4), y.vals=c(.35, .6), lab=c("TSS", "TES"))
abline(h=0.5, lty=2)
```


Quantification by gene flank and body
--------------------------------------------------------

### Difference
Construct position matrices for each cell type divided into expression quartiles
```
positionMatrix.group("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
positionMatrix.group("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
positionMatrix.group("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
```
Load 5hmC matrices and compute mean flank and mid values
```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/strand2.R"))
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/ggplot.R"))
hmc.list <- lapply(c("omp", "ngn", "icam"), function(ct) lapply(c(0,2,3,4), function(x) read.delim(paste("~/s2/analysis/profiles/norm/strand_diff/mean/gene_whole_W200N50F50_chr/images/",ct,"_hmc_120424_rmdup_plus_", ct, "_hmc_120424_rmdup_minus_W100_S25_", ct, "_quartiles_", x, sep=""), header=F, row.names=1)))
for(i in 1:length(hmc.list)) {names(hmc.list[[i]]) <- c("0", "2", "3", "4")}
hmc.list.df <- lapply(hmc.list, compute_mean_gene_set)
names(hmc.list.df) <- c("omp", "ngn", "icam")
hmc.list.df2 <- ldply(hmc.list.df)

hmc.list.df2[,2] <- as.factor(hmc.list.df2[,2])
levels(hmc.list.df2[,2]) <-c("0-25%", "25-50%", "50-75%", "75-100%")
hmc.fac <- factor(1:3, labels=c("omp", "ngn", "icam"))
hmc.list.df2[,1] <- hmc.fac[match(as.character(hmc.list.df2[,1]), as.character(hmc.fac))]
levels(hmc.list.df2[,1]) <- c("mOSN", "GBC", "HBC")
```

Plot mean value, split by grouping
```{r omp_ngn_icam_hmc_strand_diff_flank_body, dev='pdf', fig.height=6, fig.width=4.5}
theme_set(theme_bw())
hmc.list.gg <- ggplot(hmc.list.df2, aes(pos, val, fill=.id, color=.id))
hmc.list.gg <- hmc.list.gg + stat_summary(geom="bar", fun.y="mean") + stat_sum_df("mean_cl_normal", geom="errorbar") + facet_grid(.id~group) + scale_fill_grey() + scale_color_grey() 
hmc.list.gg <- hmc.list.gg + theme(legend.position="none") + ylab("Coding - Template 5hmC") + xlab("")
hmc.list.gg

```

Just mOSN data
```{r omp_hmc_strand_diff_flank_body, dev=c("png","pdf"), fig.height=3, fig.width=4.5}
theme_set(theme_bw())
hmc.list.gg <- ggplot(hmc.list.df2[hmc.list.df2$.id=="mOSN",], aes(pos, val, fill=.id, color=.id))
hmc.list.gg <- hmc.list.gg + stat_summary(geom="bar", fun.y="mean") + stat_sum_df("mean_cl_normal", geom="errorbar") + facet_grid(.~group) + scale_fill_grey() + scale_color_grey() 
hmc.list.gg <- hmc.list.gg + theme(legend.position="none") + ylab("Coding - Template 5hmC") + xlab("") + coord_cartesian(ylim=c(-.1, .025))
hmc.list.gg

```

Wilcoxon p-values for Body/Flank comparisons
```{r}
sapply(levels(hmc.list.df2$.id), function(ct) sapply(levels(hmc.list.df2$group), function(x) with(hmc.list.df2[hmc.list.df2$.id==ct & hmc.list.df2$group==x,], wilcox.test(val[pos=="Body"], val[pos=="Flank"])$p.value)))

```

### Fraction 
```
positionMatrix.group("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_fraction/mean")
```

```{r}
hmc.list <- lapply(c(0,2,3,4), function(x) read.delim(paste("~/s2/analysis/profiles/norm/strand_fraction/mean/gene_whole_W200N50F50_chr/images/omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25_omp_quartiles_", x, sep=""), header=F, row.names=1))
hmc.list <- lapply(hmc.list, function(x) (x - 0.5) *100)
names(hmc.list) <- c("0", "2", "3", "4")
hmc.list.df <- compute_mean_gene_set(hmc.list, "median")
#names(hmc.list.df) <- c("omp", "ngn", "icam")
#hmc.list.df2 <- ldply(hmc.list.df)

#hmc.list.df2[,2] <- as.factor(hmc.list.df2[,2])
levels(hmc.list.df[,1]) <-c("0-25%", "25-50%", "50-75%", "75-100%")
#hmc.fac <- factor(1:3, labels=c("omp", "ngn", "icam"))
#hmc.list.df2[,1] <- hmc.fac[match(as.character(hmc.list.df2[,1]), as.character(hmc.fac))]
#levels(hmc.list.df2[,1]) <- c("mOSN", "GBC", "HBC")
```

Just mOSN data
```{r omp_hmc_strand_fraction_flank_body, dev=c("png","pdf"), fig.height=3, fig.width=4.5}
theme_set(theme_bw())
hmc.list.gg <- ggplot(hmc.list.df, aes(pos, val))
hmc.list.gg <- hmc.list.gg + stat_summary(geom="bar", fun.y="mean") + stat_sum_df("mean_cl_normal", geom="errorbar") + facet_grid(.~group) + scale_fill_grey() + scale_color_grey() 
hmc.list.gg <- hmc.list.gg + theme(legend.position="none") + ylab("((Coding - Template) / Total) - 0.5") + xlab("") #+ coord_cartesian(ylim=c(-.05, .03))
hmc.list.gg

```

Wilcoxon p-values for Body/Flank comparisons
```{r}
sapply(levels(hmc.list.df$group), function(x) with(hmc.list.df[hmc.list.df$group==x,], wilcox.test(val[pos=="Body"], val[pos=="Flank"])$p.value))

```

