Cytosine strand bias
========================================================

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/seqUtil.R"))
```

### Full TSS set
Load TSS bed (-1kb to +1kb)
```{r}
tss <- read.delim("~/lib/features_general/refgene_-1kbTSS+1kb", header=F)
```

Extract sequences.
```{r}
tss.fa <- getSeq.bed(tss[1:10,])
```

#### Compute cytosine dinucleotide positions
```
tss.fa.c.both <- computeFrequencies(tss.fa, dicyto, fname="refgene_-1kbTSS+1kb_dicyto")
```

Subtract coding - template
```{r}
tss.fa.c.both <- read.delim("refgene_-1kbTSS+1kb_dicyto")
tss.fa.c.both <- tss.fa.c.both[-3,] # Remove CG 
tss.fa.c.both.sub <- laply(c(1:3), function(x) tss.fa.c.both[x,] - tss.fa.c.both[x+3,])
```

Plot
```{r "refgene_-1kbTSS+1kb_dicyto_coding_sub_template", dev=c("png", "pdf")}
plot(1,1, xlim=c(1,2000), ylim=c(-1,1), type="n")
sapply(1:3, function(x) lines(1:2000, tss.fa.c.both.sub[x,], col=x))
legend(1, 1, legend=c(dicyto[1:4,1]), col=1:4, lty=1, horiz=T)

```

#### Compute cytosine positions
```
tss.fa.mono <- computeFrequencies(tss.fa, mononuc, fname="refgene_-1kbTSS+1kb_mono", norm=FALSE)
```

Subtract C from G (Coding - Template)
```{r}
tss.fa.mono <- read.delim("refgene_-1kbTSS+1kb_mono")
tss.fa.mono.sub <- tss.fa.mono[2,] - tss.fa.mono[3,]
```

Plot
```{r "refgene_-1kbTSS+1kb_c_coding_sub_template", dev=c("png", "pdf")}
plot(1,1, xlim=c(1,2000), ylim=c(-1,1), type="n")
lines(1:2000, tss.fa.mono.sub)
```

### Top 10% mOSN expressors
Make deciles
```
rna <- readRDS("~/s2/analysis/rna/rdata/omp_ott3_rmrna_masked_uq_1log2.rds")
rownames(rna) <- rna$gene
rna.nz <- rna[rna[,2]>0,]
source("~/src/seqAnalysis/R/features.R")
rna.dec <- splitByQ(rna.nz, 2, q=seq(0, 1, .1), fname="~/storage/analysis/group2/omp_rmrna_gt0_deciles")
tss.10 <- tss[tss[,4] %in% rna.dec[rna.dec[,2]==10,1],]
write.table(tss.10, file="~/lib/features_general/refgene_-1kbTSS+1kb_omp_rmrna_gt0_deciles_10", quote=F, sep="\t", row.names=F, col.names=F)
```
Load TSS bed (-1kb to +1kb)
```{r}
tss <- read.delim("~/lib/features_general/refgene_-1kbTSS+1kb_omp_rmrna_gt0_deciles_10", header=F)
```

Extract sequences.
```{r}
tss.fa <- getSeq.bed(tss[1:10,])
```

#### Compute cytosine dinucleotide positions
```
tss.fa.c.both <- computeFrequencies(tss.fa, dicyto, fname="refgene_-1kbTSS+1kb_omp_rmrna_gt0_deciles_10_dicyto")
```

Subtract coding - template
```{r}
tss.fa.c.both <- read.delim("refgene_-1kbTSS+1kb_omp_rmrna_gt0_deciles_10_dicyto")
tss.fa.c.both <- tss.fa.c.both[-3,] # Remove CG 
tss.fa.c.both.sub <- laply(1:4, function(x) tss.fa.c.both[x,] - tss.fa.c.both[x+4,])
```

Plot
```{r "refgene_-1kbTSS+1kb_omp_rmrna_gt0_deciles_10_dicyto_coding_sub_template", dev=c("png", "pdf")}
plot(1,1, xlim=c(1,2000), ylim=c(-1,1), type="n")
sapply(1:4, function(x) lines(1:2000, tss.fa.c.both.sub[x,], col=x))
legend(1, 1, legend=c(dicyto[1:4,1]), col=1:4, lty=1, horiz=T)

```

#### Compute cytosine positions
```
tss.fa.mono <- computeFrequencies(tss.fa, mononuc, fname="refgene_-1kbTSS+1kb_mono", norm=FALSE)
```

Subtract C from G (Coding - Template)
```{r}
tss.fa.mono <- read.delim("refgene_-1kbTSS+1kb_mono")
tss.fa.mono.sub <- tss.fa.mono[2,] - tss.fa.mono[3,]
```

Plot
```{r "refgene_-1kbTSS+1kb_omp_rmrna_gt0_deciles_10_c_coding_sub_template", dev=c("png", "pdf")}
plot(1,1, xlim=c(1,2000), ylim=c(-1,1), type="n")
lines(1:2000, tss.fa.mono.sub)
```