5hmC/5mC/mRNA strand asymmetry
========================================================

Gene profiles
--------------------------------------------------------
### Difference 

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/profiles2.R"))
```

### First try with full data set, do not remove outliers
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
makeProfile2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean")
```
#### OMP 5hmC Coding - Template
```{r}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean", cols=col4_mod, wsize=200, fname="manual", y.vals=c(-.3, .2))
```
#### Neurog 5hmC Coding - Template
```{r}
plot2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean", cols=col4_mod, wsize=200, fname="manual", y.vals=c(-.3, .2))
```

#### Icam 5hmC Coding - Template
```{r}
plot2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean", cols=col4_mod, wsize=200, fname="manual", y.vals=c(-.3, .2))
```

### Top/bottom 2% removed at each position
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_diff/mean", rm.outliers=0.02)
```
#### OMP 5hmC Coding - Template
```{r, fig.width=9}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,4), y.vals=c(-.2, .1))
```
#### Neurog 5hmC Coding - Template
```{r, fig.width=9}
plot2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,4), y.vals=c(-.2, .1))
```

#### Icam 5hmC Coding - Template
```{r, fig.width=9}
plot2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles_trim0.02", data_type="strand_diff/mean", cols=col4_mod[c(2,4)], wsize=200, fname="manual", group2_col=c(2,4), y.vals=c(-.2, .1))
```

### Fraction

### Top/bottom 2% removed at each position
```
makeProfile2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "omp_mc_rmdup_plus_omp_mc_rmdup_minus_W100_S25", group2="omp_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "ngn_mc_rmdup_plus_ngn_mc_rmdup_minus_W100_S25", group2="ngn_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
makeProfile2("gene_whole_W200N50F50_chr", "icam_mc_rmdup_plus_icam_mc_rmdup_minus_W100_S25", group2="icam_quartiles", data_type="strand_fraction/mean", rm.outliers=0.02)
```

#### OMP 5hmC (Coding - Template)/Total
```{r}
plot2("gene_whole_W200N50F50_chr", "omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", group2="omp_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(1,4)], wsize=200, fname="manual", group2_col=c(1,4), y.vals=c(.3, .7))
abline(h=0.5, lty=2)
```
#### Neurog 5hmC (Coding - Template)/Total
```{r}
plot2("gene_whole_W200N50F50_chr", "ngn_hmc_120424_rmdup_plus_ngn_hmc_120424_rmdup_minus_W100_S25", group2="ngn_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(1,4)], wsize=200, fname="manual", group2_col=c(1,4), y.vals=c(.3, .7))
abline(h=0.5, lty=2)
```

#### Icam 5hmC (Coding - Template)/Total
```{r}
#plot2("gene_whole_W200N50F50_chr", "icam_hmc_120424_rmdup_plus_icam_hmc_120424_rmdup_minus_W100_S25", group2="icam_quartiles_trim0.02", data_type="strand_fraction/mean", cols=col4_mod[c(1,4)], wsize=200, fname="manual", group2_col=c(1,4), y.vals=c(.3, .7))
```

TSS Heatmaps
--------------------------------------------------------
Matrix of plus/minus strand differences for a given sample. For genes, plus/minus strand designation adjusted as coding/template strand.
First order MOE Dnmt3a WT polyA-RNA-seq by coding/template difference within the region -5 kb to 1.25 kb upstream of the TSS.

```{r}
suppressPackageStartupMessages(source("~/src/seqAnalysis/R/image.R"))
moe.rna <- read.delim("~/s2/analysis/profiles/norm/strand_diff/mean/refGene_noRandom_order_outsides2_tss_W25F200_chr/images/moe_d3a_wt_mrna_plus_sub_minus_1log_na_omit", header=T)
moe.rna.up.mean <- apply(moe.rna[,1:150], 1, mean)
moe.rna.up.mean <- sort(moe.rna.up.mean)
```

Order original matrix by these values and plot to check. Plot saved to "refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_moe_d3a_wt_mrna_plus_sub_minus_1log_na_omit_order_-5kbTo-1250bp.pdf"

```{r}
moe.rna.ord.moe.rna.up <- moe.rna[match(names(moe.rna.up.mean), rownames(moe.rna)),]
MP.heat(as.matrix(moe.rna.ord.moe.rna.up), range=c(-.02, .02), average=50)

```

Order MOE Dnmt3a WT 5hmC matrix by RNA coding/template difference. Plot in "refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_moe_d3a_wt_hmc_plus_sub_minus_order_-5kbTo-1250bp.pdf"

```{r}
moe.hmc <- makeImage("moe_d3a_wt_hmc_plus_sub_minus", "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE)
moe.hmc.ord.moe.rna.up <- moe.hmc[match(names(moe.rna.up.mean), rownames(moe.hmc)),]
MP.heat(as.matrix(moe.hmc.ord.moe.rna.up), range=c(-.005, .005), average=100)

```

Repeat with developmental celltype data. First construct difference matrices. 

```
positionMatrix.all(anno="refGene_noRandom_order_outsides2_tss_W25F200_chr", "strand_diff/mean")

```

Test OMP 5hmC dataset. Heatmap saved in "refGene_noRandom_order_outsides2_tss_W25F200_chr_strand_diff_mean_omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25_order_-5kbTo-1250bp.pdf"

#### OMP 5hmC Coding - Template
```{r}
omp.hmc <- makeImage("omp_hmc_120424_rmdup_plus_omp_hmc_120424_rmdup_minus_W100_S25", "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE)
omp.hmc.ord.moe.rna.up <- omp.hmc[match(names(moe.rna.up.mean), rownames(omp.hmc)),]
MP.heat(as.matrix(omp.hmc.ord.moe.rna.up), range=c(-.25, .25), average=100)

```

Repeat with other sets
```{r}
pos.hmc <- lapply(c("omp", "ngn", "icam"), function(x) makeImage(paste(x, "hmc_120424_rmdup_plus", x, "hmc_120424_rmdup_minus_W100_S25", sep="_"), "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE))
pos.hmc.ord <- lapply(pos.hmc, function(x) x[match(names(moe.rna.up.mean), rownames(x)),])
pos.mc <- lapply(c("omp", "ngn", "icam"), function(x) makeImage(paste(x, "mc_rmdup_plus", x, "mc_rmdup_minus_W100_S25", sep="_"), "refGene_noRandom_order_outsides2_tss_W25F200_chr", data_type="strand_diff/mean", image=FALSE))
pos.mc.ord <- lapply(pos.mc, function(x) x[match(names(moe.rna.up.mean), rownames(x)),])
```

#### Neurog1 5hmC Coding - Template
```{r, fig.width=6, fig.height=6}
MP.heat(as.matrix(pos.hmc.ord[[2]]), range=c(-.25, .25), average=100)
```

#### Icam 5hmC Coding - Template
```{r, fig.width=6, fig.height=6}
MP.heat(as.matrix(pos.hmc.ord[[3]]), range=c(-.25, .25), average=100)
```

#### OMP 5mC Coding - Template
```{r, fig.width=6, fig.height=6}
MP.heat(as.matrix(pos.mc.ord[[1]]), range=c(-.25, .25), average=100)
```

#### Neurog 5mC Coding - Template
```{r, fig.width=6, fig.height=6}
MP.heat(as.matrix(pos.mc.ord[[2]]), range=c(-.25, .25), average=100)
```

#### Icam 5mC Coding - Template
```{r, fig.width=6, fig.height=6}
MP.heat(as.matrix(pos.mc.ord[[3]]), range=c(-.25, .25), average=100)
```

